---
title: "analysis_Theron"
author: "Theron Palmer"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


# Libraries used in the analysis

```{r}

library(ggplot2)
library(knitr)
library(dplyr)
library(org.Mm.eg.db)
library(DT)
library(GeneOverlap)
library(GO.db)
library(KEGGREST)
library(KEGG.db)
library(fgsea)
library(maftools)
library(pheatmap)
library(ensembldb)
library(stringr)
library(ensembldb)
library(BSgenome.Mmusculus.GENCODE.GRCm38.102)
library(biomaRt)
library(ggpubr)

```

# Loading in the necessary data

```{r}

base_dir <- "/media/theron/My_Passport/Ali_data/HTMBmice_RNAseq_Data/MB01JHU504/MB01JHU504_000_analysis/DESeq2/refseq_genes"
PD1_vs_combo <- read.table(sprintf("%s/%s",base_dir,"PD1_vs_Combo_genes_DESeq2.txt"),header=T)
untreated_vs_combo <- read.table(sprintf("%s/%s",base_dir,"Untreated_vs_Combo_genes_DESeq2.txt"),header=T)
untreated_vs_PD1 <- read.table(sprintf("%s/%s",base_dir,"Untreated_vs_PD1_genes_DESeq2.txt"),header=T)

```

# PD1 vs Combo (PD1/Combo)

## Differential Expression Data

```{r}

which_sig <- vapply(as.numeric(PD1_vs_combo$PD1_vs_Combo_pvalue),function(val){
  if (is.na(val)){
    return("Insig")
  }
  if (val <= 0.05){
    return("Sig")
  } else {
    return("Insig")
  }},character(1))
PD1_vs_combo$significance_pval <- which_sig

which_sig <- vapply(PD1_vs_combo$PD1_vs_Combo_padj,function(val){
  if (is.na(val)){
    return("Insig")
  }
  if (val <= 0.05){
    return("Sig")
  } else {
    return("Insig")
  }},character(1))
PD1_vs_combo$significance_padj <- which_sig

datatable(PD1_vs_combo)

```


## Volcano Plots

```{r}

ggplot(PD1_vs_combo,aes(x=PD1_vs_Combo_log2FoldChange, y=-log10(PD1_vs_Combo_pvalue), color = significance_pval))+
  geom_text(label=PD1_vs_combo$gene_symbol)
ggplot(PD1_vs_combo,aes(x=PD1_vs_Combo_log2FoldChange, y=-log10(PD1_vs_Combo_padj), color = significance_padj))+
  geom_text(label=PD1_vs_combo$gene_symbol)

```
## gsea results on GO and KEGG terms

```{r}

symbol_to_entrez <- as.list(org.Mm.egALIAS2EG)
PD1_vs_combo$entrez <- symbol_to_entrez[PD1_vs_combo$gene_symbol]

SYMBOLToGO <- mapIds(org.Mm.eg.db,keys=PD1_vs_combo$gene_symbol,column='GO',keytype = 'SYMBOL',multiVals = list)
GOToSYMBOL <- sapply(reverseSplit(SYMBOLToGO),unique)
GOToSYMBOL <- GOToSYMBOL[sapply(GOToSYMBOL,length)>5]

SYMBOLToKEGG <- mapIds(org.Mm.eg.db,keys=PD1_vs_combo$gene_symbol,column='PATH',keytype = 'SYMBOL',multiVals = list)
KEGGToSYMBOL <- sapply(reverseSplit(SYMBOLToKEGG),unique)
KEGGToSYMBOL <- KEGGToSYMBOL[sapply(KEGGToSYMBOL,length)>5]

diff_dat_filt <- PD1_vs_combo %>% dplyr::filter(!is.na(PD1_vs_Combo_log2FoldChange) & !is.na(PD1_vs_Combo_pvalue))
ranks <- diff_dat_filt$PD1_vs_Combo_log2FoldChange*-log10(diff_dat_filt$PD1_vs_Combo_pvalue)
names(ranks)<-diff_dat_filt$gene_symbol
ranks<-ranks[unname(!is.na(ranks))]
# ranks<-rank(ranks,ties.method = "random")
fgseaRes_GO <- fgsea(GOToSYMBOL, ranks, eps=0,scoreType="pos")
fgseaRes_GO<-cbind(sapply(c('ONTOLOGY','TERM','DEFINITION'),
                        function(x){mapIds(GO.db,keys=fgseaRes_GO$pathway,keytype='GOID',column=x)}),fgseaRes_GO)
fgseaRes_KEGG <- fgsea(KEGGToSYMBOL, ranks, eps=0,scoreType="pos")
fgseaRes_KEGG <- cbind(KEGG.Name=unlist(as.list(KEGGPATHID2NAME)[fgseaRes_KEGG$pathway]),
                   fgseaRes_KEGG)

pathways<- readRDS("/media/theron/My_Passport/LM_LMT_LUCIANE_cellranger/references/gene_sets/mouse_hallmark.rds")
pathways_list <- lapply(unique(pathways$gs_name),function(pathway){
  pathway_small <- pathways %>% dplyr::filter(gs_name == pathway)
  return(pathway_small$gene_symbol)
})
names(pathways_list)<-unique(pathways$gs_name)

fgseaRes_HALLMARK <- fgsea(pathways_list, ranks, eps=0)
fgseaRes_HALLMARK <- fgseaRes_HALLMARK %>% dplyr::filter(padj <= 0.05)

```

### GO GSEA
```{r}

GO_table <- fgseaRes_GO %>% dplyr::filter(padj <= 0.05)
GO_table<-GO_table[,c("TERM","DEFINITION","padj","NES","size")]
datatable(GO_table)

```

### KEGG GSEA
```{r}

KEGG_table <- fgseaRes_KEGG %>% dplyr::filter(padj <= 0.05)
KEGG_table<-KEGG_table[,c("KEGG.Name","padj","NES","size")]
datatable(KEGG_table)

```

### HALLMARK GSEA
```{r}

datatable(fgseaRes_HALLMARK[,c(1,3,6,7)])

```


# Untreated vs Combo (Untreated/Combo) 

## Differential Expression Data

```{r}

which_sig <- vapply(as.numeric(untreated_vs_combo$Untreated_vs_Combo_pvalue),function(val){
  if (is.na(val)){
    return("Insig")
  }
  if (val <= 0.05){
    return("Sig")
  } else {
    return("Insig")
  }},character(1))
untreated_vs_combo$significance_pval <- which_sig

which_sig <- vapply(untreated_vs_combo$Untreated_vs_Combo_padj,function(val){
  if (is.na(val)){
    return("Insig")
  }
  if (val <= 0.05){
    return("Sig")
  } else {
    return("Insig")
  }},character(1))
untreated_vs_combo$significance_padj <- which_sig

datatable(untreated_vs_combo)

```

## Volcano Plots

```{r}

ggplot(untreated_vs_combo,aes(x=Untreated_vs_Combo_log2FoldChange, y=-log10(Untreated_vs_Combo_pvalue), color = significance_pval))+
  geom_text(label=untreated_vs_combo$gene_symbol)
ggplot(untreated_vs_combo,aes(x=Untreated_vs_Combo_log2FoldChange, y=-log10(Untreated_vs_Combo_padj), color = significance_padj))+
  geom_text(label=untreated_vs_combo$gene_symbol)

```

## gsea results on GO and KEGG terms

```{r}

symbol_to_entrez <- as.list(org.Mm.egALIAS2EG)
untreated_vs_combo$entrez <- symbol_to_entrez[untreated_vs_combo$gene_symbol]

SYMBOLToGO <- mapIds(org.Mm.eg.db,keys=untreated_vs_combo$gene_symbol,column='GO',keytype = 'SYMBOL',multiVals = list)
GOToSYMBOL <- sapply(reverseSplit(SYMBOLToGO),unique)
GOToSYMBOL <- GOToSYMBOL[sapply(GOToSYMBOL,length)>5]

SYMBOLToKEGG <- mapIds(org.Mm.eg.db,keys=untreated_vs_combo$gene_symbol,column='PATH',keytype = 'SYMBOL',multiVals = list)
KEGGToSYMBOL <- sapply(reverseSplit(SYMBOLToKEGG),unique)
KEGGToSYMBOL <- KEGGToSYMBOL[sapply(KEGGToSYMBOL,length)>5]

diff_dat_filt <- untreated_vs_combo %>% dplyr::filter(!is.na(Untreated_vs_Combo_log2FoldChange) & !is.na(Untreated_vs_Combo_pvalue))
ranks <- diff_dat_filt$Untreated_vs_Combo_log2FoldChange*-log10(diff_dat_filt$Untreated_vs_Combo_pvalue)
names(ranks)<-diff_dat_filt$gene_symbol
ranks<-ranks[unname(!is.na(ranks))]
# ranks<-rank(ranks,ties.method = "random")
fgseaRes_GO <- fgsea(GOToSYMBOL, ranks, eps=0,scoreType="pos")
fgseaRes_GO<-cbind(sapply(c('ONTOLOGY','TERM','DEFINITION'),
                        function(x){mapIds(GO.db,keys=fgseaRes_GO$pathway,keytype='GOID',column=x)}),fgseaRes_GO)
fgseaRes_KEGG <- fgsea(KEGGToSYMBOL, ranks, eps=0,scoreType="pos")
fgseaRes_KEGG <- cbind(KEGG.Name=unlist(as.list(KEGGPATHID2NAME)[fgseaRes_KEGG$pathway]),
                   fgseaRes_KEGG)

pathways_list <- readRDS("/media/theron/My_Passport/LM_LMT_LUCIANE_cellranger/references/gene_sets/pathways_list_ensembl.rds")
fgseaRes_HALLMARK <- fgsea(pathways_list, ranks, eps=0)
fgseaRes_HALLMARK <- fgseaRes_HALLMARK %>% dplyr::filter(padj <= 0.05)

```

### GO GSEA
```{r}

GO_table <- fgseaRes_GO %>% dplyr::filter(padj <= 0.05)
GO_table<-GO_table[,c("TERM","DEFINITION","padj","NES","size")]
datatable(GO_table)

```

### KEGG GSEA
```{r}

KEGG_table <- fgseaRes_KEGG %>% dplyr::filter(padj <= 0.05)
KEGG_table<-KEGG_table[,c("KEGG.Name","padj","NES","size")]
datatable(KEGG_table)

```

### HALLMARK Pathway GSEA
```{r}

datatable(fgseaRes_HALLMARK[,c(1,3,6,7)])

```

# Untreated vs PD1 (Untreated/PD1) 

## Differential Expression Data

```{r}

which_sig <- vapply(as.numeric(untreated_vs_PD1$Untreated_vs_PD1_pvalue),function(val){
  if (is.na(val)){
    return("Insig")
  }
  if (val <= 0.05){
    return("Sig")
  } else {
    return("Insig")
  }},character(1))
untreated_vs_PD1$significance_pval <- which_sig

which_sig <- vapply(untreated_vs_PD1$Untreated_vs_PD1_padj,function(val){
  if (is.na(val)){
    return("Insig")
  }
  if (val <= 0.05){
    return("Sig")
  } else {
    return("Insig")
  }},character(1))
untreated_vs_PD1$significance_padj <- which_sig
datatable(untreated_vs_PD1)

```


## Volcano Plots

```{r}

ggplot(untreated_vs_PD1,aes(x=Untreated_vs_PD1_log2FoldChange, y=-log10(Untreated_vs_PD1_pvalue), color = significance_pval))+
  geom_text(label=untreated_vs_PD1$gene_symbol)
ggplot(untreated_vs_PD1,aes(x=Untreated_vs_PD1_log2FoldChange, y=-log10(Untreated_vs_PD1_padj), color = significance_padj))+
  geom_text(label=untreated_vs_PD1$gene_symbol)

```


## gsea results on GO,KEGG, and Hallmark Pathway terms

```{r}

symbol_to_entrez <- as.list(org.Mm.egALIAS2EG)
untreated_vs_PD1$entrez <- symbol_to_entrez[untreated_vs_PD1$gene_symbol]

SYMBOLToGO <- mapIds(org.Mm.eg.db,keys=untreated_vs_PD1$gene_symbol,column='GO',keytype = 'SYMBOL',multiVals = list)
GOToSYMBOL <- sapply(reverseSplit(SYMBOLToGO),unique)
GOToSYMBOL <- GOToSYMBOL[sapply(GOToSYMBOL,length)>5]

SYMBOLToKEGG <- mapIds(org.Mm.eg.db,keys=untreated_vs_PD1$gene_symbol,column='PATH',keytype = 'SYMBOL',multiVals = list)
KEGGToSYMBOL <- sapply(reverseSplit(SYMBOLToKEGG),unique)
KEGGToSYMBOL <- KEGGToSYMBOL[sapply(KEGGToSYMBOL,length)>5]

diff_dat_filt <- untreated_vs_PD1 %>% dplyr::filter(!is.na(Untreated_vs_PD1_log2FoldChange) & !is.na(Untreated_vs_PD1_pvalue))
ranks <- diff_dat_filt$Untreated_vs_PD1_log2FoldChange*-log10(diff_dat_filt$Untreated_vs_PD1_pvalue)
names(ranks)<-diff_dat_filt$gene_symbol
ranks<-ranks[unname(!is.na(ranks))]
# ranks<-rank(ranks,ties.method = "random")
fgseaRes_GO <- fgsea(GOToSYMBOL, ranks, eps=0,scoreType="pos")
fgseaRes_GO<-cbind(sapply(c('ONTOLOGY','TERM','DEFINITION'),
                        function(x){mapIds(GO.db,keys=fgseaRes_GO$pathway,keytype='GOID',column=x)}),fgseaRes_GO)
fgseaRes_KEGG <- fgsea(KEGGToSYMBOL, ranks, eps=0,scoreType="pos")
fgseaRes_KEGG <- cbind(KEGG.Name=unlist(as.list(KEGGPATHID2NAME)[fgseaRes_KEGG$pathway]),
                   fgseaRes_KEGG)

pathways_list <- readRDS("/media/theron/My_Passport/LM_LMT_LUCIANE_cellranger/references/gene_sets/pathways_list_ensembl.rds")
fgseaRes_HALLMARK <- fgsea(pathways_list, ranks, eps=0)
fgseaRes_HALLMARK <- fgseaRes_HALLMARK %>% dplyr::filter(padj <= 0.05)

```

### GO GSEA
```{r}

GO_table <- fgseaRes_GO %>% dplyr::filter(padj <= 0.05)
GO_table<-GO_table[,c("TERM","DEFINITION","padj","NES","size")]
datatable(GO_table)

```

### KEGG GSEA
```{r}

KEGG_table <- fgseaRes_KEGG %>% dplyr::filter(padj <= 0.05)
KEGG_table<-KEGG_table[,c("KEGG.Name","padj","NES","size")]
datatable(KEGG_table)

```

### HALLMARK Pathway GSEA
```{r}

datatable(fgseaRes_HALLMARK[,c(1,3,6,7)])

```

# Exploring Whole Exome mutation data- maf format

## Those mutations with differential expression per comparison

```{r}

maf_file <- "/media/theron/My_Passport/Ali_data/WES Data for 4T1MIS/MB01JHU503/MB01JHU503_000_analysis/MAF/DNA_4TIMSI_haplotypecaller.maf"
ali_maf = read.maf(maf_file)
ali_gene_summ = getGeneSummary(ali_maf)
rownames(ali_gene_summ) <- ali_gene_summ$Hugo_Symbol

rownames(PD1_vs_combo) <- PD1_vs_combo$gene_symbol
rownames(untreated_vs_combo) <- untreated_vs_combo$gene_symbol
rownames(untreated_vs_PD1) <- untreated_vs_PD1$gene_symbol

ali_gene_summ <- cbind(ali_gene_summ,PD1_vs_combo[ali_gene_summ$Hugo_Symbol,c("PD1_vs_Combo_log2FoldChange","significance_pval","significance_padj")])
ali_gene_summ <- cbind(ali_gene_summ,untreated_vs_combo[ali_gene_summ$Hugo_Symbol,c("Untreated_vs_Combo_log2FoldChange","significance_pval","significance_padj")])
ali_gene_summ <- cbind(ali_gene_summ,untreated_vs_PD1[ali_gene_summ$Hugo_Symbol,c("Untreated_vs_PD1_log2FoldChange","significance_pval","significance_padj")])

cols <- colnames(ali_gene_summ)
cols[seq(15,22)]<-c("pc_significance_pval","pc_significance_padj",
                    "Untreated_vs_Combo_log2FoldChange","uc_significance_pval","uc_significance_padj",
                    "Untreated_vs_PD1_log2FoldChange","up_significance_pval","up_significance_padj")
colnames(ali_gene_summ) <- cols
datatable(ali_gene_summ)

```

## PD1 vs Combo 
```{r}

ali_gene_summ_PD1 <- ali_gene_summ %>% dplyr::filter(pc_significance_pval=="Sig")
ggplot(ali_gene_summ_PD1,aes(y=log2(Missense_Mutation),x=PD1_vs_Combo_log2FoldChange))+
  geom_text(label=ali_gene_summ_PD1$Hugo_Symbol)+labs(title="pval Significant Genes")
datatable(ali_gene_summ_PD1)

ali_gene_summ_PD1 <- ali_gene_summ %>% dplyr::filter(pc_significance_padj=="Sig")
ggplot(ali_gene_summ_PD1,aes(y=log2(Missense_Mutation),x=PD1_vs_Combo_log2FoldChange))+
  geom_text(label=ali_gene_summ_PD1$Hugo_Symbol)+labs(title="padj Significant Genes")
datatable(ali_gene_summ_PD1)

```

## Untreated vs Combo

```{r}

ali_gene_summ_uc <- ali_gene_summ %>% dplyr::filter(uc_significance_pval=="Sig")
ggplot(ali_gene_summ_uc,aes(y=log2(Missense_Mutation),x=Untreated_vs_Combo_log2FoldChange))+
  geom_text(label=ali_gene_summ_uc$Hugo_Symbol)+labs(title="pval Significant Genes")
datatable(ali_gene_summ_uc)

ali_gene_summ_uc <- ali_gene_summ %>% dplyr::filter(uc_significance_padj=="Sig")
ggplot(ali_gene_summ_uc,aes(y=log2(Missense_Mutation),x=Untreated_vs_Combo_log2FoldChange))+
  geom_text(label=ali_gene_summ_uc$Hugo_Symbol)+labs(title="padj Significant Genes")
datatable(ali_gene_summ_uc)

```

## Untreated vs PD1
```{r}

ali_gene_summ_up <- ali_gene_summ %>% dplyr::filter(up_significance_pval=="Sig")
ggplot(ali_gene_summ_up,aes(y=log2(Missense_Mutation),x=Untreated_vs_PD1_log2FoldChange))+
  geom_text(label=ali_gene_summ_up$Hugo_Symbol)+labs(title="pval Significant Genes")
datatable(ali_gene_summ_up)

ali_gene_summ_up <- ali_gene_summ %>% dplyr::filter(up_significance_padj=="Sig")
ggplot(ali_gene_summ_up,aes(y=log2(Missense_Mutation),x=Untreated_vs_PD1_log2FoldChange))+
  geom_text(label=ali_gene_summ_up$Hugo_Symbol)+labs(title="padj Significant Genes")
datatable(ali_gene_summ_up)

```

## Gene expression of Mutated Genes Per Sample

```{r}

tpm_gene_expression_file <- "/media/theron/My_Passport/Ali_data/HTMBmice_RNAseq_Data/MB01JHU504/MB01JHU504_000_analysis/RSEM/tables/genes/genes_tpm_all_samples_norm.txt"
tpm_gene_expression <- read.table(tpm_gene_expression_file,header=T,sep="\t")

maf_file <- "/media/theron/My_Passport/Ali_data/WES Data for 4T1MIS/MB01JHU503/MB01JHU503_000_analysis/MAF/DNA_4TIMSI_haplotypecaller.maf"
ali_maf = read.maf(maf_file)
ali_gene_summ = as.data.frame(getGeneSummary(ali_maf))
rownames(ali_gene_summ) <- ali_gene_summ$Hugo_Symbol
missense_dat <- ali_gene_summ[tpm_gene_expression$gene_id,]
missense_dat <- missense_dat[complete.cases(missense_dat),]

rownames(tpm_gene_expression) <- tpm_gene_expression$gene_id
Missense_Mutation<-missense_dat$Missense_Mutation
tpm_gene_expression_complete <- cbind(tpm_gene_expression[rownames(missense_dat),seq(2,ncol(tpm_gene_expression))],Missense_Mutation)
tpm_gene_expression_complete <- tpm_gene_expression_complete[complete.cases(tpm_gene_expression_complete),]

combo<-apply(tpm_gene_expression_complete[,seq(6)],1,mean)
pd1<-apply(tpm_gene_expression_complete[,seq(7,12)],1,mean)
untreated<-apply(tpm_gene_expression_complete[,seq(12,ncol(tpm_gene_expression_complete))],1,mean)

Missense_Mutation<-tpm_gene_expression_complete$Missense_Mutation
average_expression<-data.frame(rownames(tpm_gene_expression_complete),
                               combo,pd1,untreated,
                               Missense_Mutation)
colnames(average_expression) <- c("gene","C_TPM_AV","P_TPM_AV","U_TPM_AV","Missense_Mutation")
average_expression_linear<-data.frame(rep(rownames(tpm_gene_expression_complete),3),c(combo,pd1,untreated),
                               rep(Missense_Mutation,3),
                               c(rep("combo",length(combo)),
                               rep("pd1",length(pd1)),
                               rep("untreated",length(untreated))))
colnames(average_expression_linear)<-c("gene","TPM_expression","Missense_Mutation","type")

average_expression$expression_order <- vapply(seq(nrow(average_expression)),function(row_val){
  vals<-average_expression[row_val, c("C_TPM_AV","P_TPM_AV","U_TPM_AV")]
  if (vals$C_TPM_AV < vals$P_TPM_AV & vals$P_TPM_AV < vals$U_TPM_AV){
    return(c("combo<pd1<untreated"))
  } else if (vals$C_TPM_AV < vals$U_TPM_AV & vals$U_TPM_AV < vals$P_TPM_AV) {
    return("combo<untreated<pd1")
  } else if (vals$P_TPM_AV < vals$C_TPM_AV & vals$C_TPM_AV < vals$U_TPM_AV){
    return("pd1<combo<untreated")
  } else if (vals$P_TPM_AV < vals$U_TPM_AV & vals$U_TPM_AV < vals$C_TPM_AV){
    return("pd1<untreated<combo")
  } else if (vals$U_TPM_AV < vals$P_TPM_AV & vals$P_TPM_AV < vals$C_TPM_AV) {
    return("untreated<pd1<combo")
  } else if (vals$U_TPM_AV < vals$C_TPM_AV & vals$C_TPM_AV < vals$P_TPM_AV) {
    return("untreated<combo<pd1")
  } else {
    return("something's equal")
  }
},character(1))

ggplot(average_expression,aes(x=expression_order,fill=expression_order))+
  geom_bar(aes(y=(..count..)/sum(..count..)))+
  theme(axis.text.x=element_blank())

ggplot(average_expression_linear,aes(x=log2(Missense_Mutation+1),y=log2(TPM_expression+1),color=type))+geom_point(shape=1)

# combo<-apply(tpm_gene_expression[,seq(2,6)],1,mean)
# combo<-scale(combo)
# pd1<-apply(tpm_gene_expression[,seq(7,12)],1,mean)
# pd1<-scale(pd1)
# untreated<-apply(tpm_gene_expression[,seq(12,ncol(tpm_gene_expression))],1,mean)
# untreated<-scale(untreated)
# 
# average_expression_all <-data.frame(rownames(tpm_gene_expression),
#                                combo,pd1,untreated)
# colnames(average_expression_all) <- c("gene","C_TPM_AV","P_TPM_AV","U_TPM_AV")
# 
# average_expression_all$expression_order <- vapply(seq(nrow(average_expression_all)),function(row_val){
#   vals<-average_expression_all[row_val, c("C_TPM_AV","P_TPM_AV","U_TPM_AV")]
#   if (vals$C_TPM_AV < vals$P_TPM_AV & vals$P_TPM_AV < vals$U_TPM_AV){
#     return(c("combo<pd1<untreated"))
#   } else if (vals$C_TPM_AV < vals$U_TPM_AV & vals$U_TPM_AV < vals$P_TPM_AV) {
#     return("combo<untreated<pd1")
#   } else if (vals$P_TPM_AV < vals$C_TPM_AV & vals$C_TPM_AV < vals$U_TPM_AV){
#     return("pd1<combo<untreated")
#   } else if (vals$P_TPM_AV < vals$U_TPM_AV & vals$U_TPM_AV < vals$C_TPM_AV){
#     return("pd1<untreated<combo")
#   } else if (vals$U_TPM_AV < vals$P_TPM_AV & vals$P_TPM_AV < vals$C_TPM_AV) {
#     return("untreated<pd1<combo")
#   } else if (vals$U_TPM_AV < vals$C_TPM_AV & vals$C_TPM_AV < vals$P_TPM_AV) {
#     return("untreated<combo<pd1")
#   } else {
#     return("something's equal")
#   }
# },character(1))
# 
# ggplot(average_expression_all,aes(x=expression_order,fill=expression_order))+
#   geom_bar(aes(y=(..count..)/sum(..count..)))+
#   theme(axis.text.x=element_blank())

```

# Exploring outlier splice junctions Combo and PD1 vs Outlier

## Filtering for significant junctions per sample

```{r}

C1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C1_pVals.txt"
C1_clusters <- read.table(C1_clusters_file,header=T)
C1_clusters$juncs <- vapply(rownames(C1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C1_clusters_sig <- C1_clusters %>% dplyr::filter(C1 <= 0.05)


C2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C2_pVals.txt"
C2_clusters <- read.table(C2_clusters_file,header=T)
C2_clusters$juncs <- vapply(rownames(C2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C2_clusters_sig <- C2_clusters %>% dplyr::filter(C2 <= 0.05)

C3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C3_pVals.txt"
C3_clusters <- read.table(C3_clusters_file,header=T)
C3_clusters$juncs <- vapply(rownames(C3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C3_clusters_sig <- C3_clusters %>% dplyr::filter(C3 <= 0.05)

C5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C5_pVals.txt"
C5_clusters <- read.table(C5_clusters_file,header=T)
C5_clusters$juncs <- vapply(rownames(C5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C5_clusters_sig <- C5_clusters %>% dplyr::filter(C5 <= 0.05)

C6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C6_pVals.txt"
C6_clusters <- read.table(C6_clusters_file,header=T)
C6_clusters$juncs <- vapply(rownames(C6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C6_clusters_sig <- C6_clusters %>% dplyr::filter(C6 <= 0.05)

C7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C7_pVals.txt"
C7_clusters <- read.table(C7_clusters_file,header=T)
C7_clusters_sig <- C7_clusters %>% dplyr::filter(C7 <= 0.05)
C7_clusters_sig$juncs <- vapply(rownames(C7_clusters_sig),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))

P1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P1_pVals.txt"
P1_clusters <- read.table(P1_clusters_file,header=T)
P1_clusters$juncs <- vapply(rownames(P1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
P1_clusters_sig <- P1_clusters %>% dplyr::filter(P1 <= 0.05)

P2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P2_pVals.txt"
P2_clusters <- read.table(P2_clusters_file,header=T)
P2_clusters$juncs <- vapply(rownames(P2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
P2_clusters_sig <- P2_clusters %>% dplyr::filter(P2 <= 0.05)

P3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P3_pVals.txt"
P3_clusters <- read.table(P3_clusters_file,header=T)
P3_clusters$juncs <- vapply(rownames(P3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
P3_clusters_sig <- P3_clusters %>% dplyr::filter(P3 <= 0.05)

P5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P5_pVals.txt"
P5_clusters <- read.table(P5_clusters_file,header=T)
P5_clusters$juncs <- vapply(rownames(P5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P5_clusters_sig <- P5_clusters %>% dplyr::filter(P5 <= 0.05)

P6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P6_pVals.txt"
P6_clusters <- read.table(P6_clusters_file,header=T)
P6_clusters$juncs <- vapply(rownames(P6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P6_clusters_sig <- P6_clusters %>% dplyr::filter(P6 <= 0.05)

P7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P7_pVals.txt"
P7_clusters <- read.table(P7_clusters_file,header=T)
P7_clusters$juncs <- vapply(rownames(P7_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P7_clusters_sig <- P7_clusters %>% dplyr::filter(P7 <= 0.05)

juncs_sig <- unique(c(C1_clusters_sig$juncs,C2_clusters_sig$juncs,
           C3_clusters_sig$juncs,C5_clusters_sig$juncs,
           C6_clusters_sig$juncs,C7_clusters_sig$juncs,
           P1_clusters_sig$juncs,P2_clusters_sig$juncs,
           P3_clusters_sig$juncs,P5_clusters_sig$juncs,
           P6_clusters_sig$juncs,P7_clusters_sig$juncs))
juncs_all <- unique(c(C1_clusters$juncs,C2_clusters$juncs,
           C3_clusters$juncs,C5_clusters$juncs,
           C6_clusters$juncs,C7_clusters$juncs,
           P1_clusters$juncs,P2_clusters$juncs,
           P3_clusters$juncs,P5_clusters$juncs,
           P6_clusters$juncs,P7_clusters$juncs))

```

## Combining the outlier splicing junctions for each type together

```{r}

all_sample_pvals <- data.frame(juncs_all)
rownames(all_sample_pvals) <- juncs_all
all_sample_pvals$C1 <- NA
all_sample_pvals[C1_clusters$juncs,"C1"]<-C1_clusters$C1
all_sample_pvals$C2 <- NA
all_sample_pvals[C2_clusters$juncs,"C2"]<-C2_clusters$C2
all_sample_pvals$C3 <- NA
all_sample_pvals[C3_clusters$juncs,"C3"]<-C3_clusters$C3
all_sample_pvals$C5 <- NA
all_sample_pvals[C5_clusters$juncs,"C5"]<-C5_clusters$C5
all_sample_pvals$C6 <- NA
all_sample_pvals[C6_clusters$juncs,"C6"]<-C6_clusters$C6
all_sample_pvals$C7 <- NA
all_sample_pvals[C7_clusters$juncs,"C7"]<-C7_clusters$C7
all_sample_pvals$P1 <- NA
all_sample_pvals[P1_clusters$juncs,"P1"]<-P1_clusters$P1
all_sample_pvals$P2 <- NA
all_sample_pvals[P2_clusters$juncs,"P2"]<-P2_clusters$P2
all_sample_pvals$P3 <- NA
all_sample_pvals[P3_clusters$juncs,"P3"]<-P3_clusters$P3
all_sample_pvals$P5 <- NA
all_sample_pvals[P5_clusters$juncs,"P5"]<-P5_clusters$P5
all_sample_pvals$P6 <- NA
all_sample_pvals[P6_clusters$juncs,"P6"]<-P6_clusters$P6
all_sample_pvals$P7 <- NA
all_sample_pvals[P7_clusters$juncs,"P7"]<-P7_clusters$P7
all_sample_pvals<-all_sample_pvals[juncs_sig,seq(2,ncol(all_sample_pvals))]

```

## Using all significant junctions, extracting psi per leafcutter cluster

```{r}

C1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C1_perind.counts.gz"
C1_clusters <- read.table(C1_clusters_file,header=T)
rownames(C1_clusters) <- C1_clusters$chrom
C1_clusters$juncs <- vapply(rownames(C1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C1_clusters_psi <- C1_clusters[rownames(C1_clusters_sig),]

C2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C2_perind.counts.gz"
C2_clusters <- read.table(C2_clusters_file,header=T)
rownames(C2_clusters) <- C2_clusters$chrom
C2_clusters$juncs <- vapply(rownames(C2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C2_clusters_psi <- C2_clusters[rownames(C2_clusters_sig),]

C3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C3_perind.counts.gz"
C3_clusters <- read.table(C3_clusters_file,header=T)
rownames(C3_clusters) <- C3_clusters$chrom
C3_clusters$juncs <- vapply(rownames(C3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C3_clusters_psi <- C3_clusters[rownames(C3_clusters_sig),]

C5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C5_perind.counts.gz"
C5_clusters <- read.table(C5_clusters_file,header=T)
rownames(C5_clusters) <- C5_clusters$chrom
C5_clusters$juncs <- vapply(rownames(C5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C5_clusters_psi <- C5_clusters[rownames(C5_clusters_sig),]

C6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C6_perind.counts.gz"
C6_clusters <- read.table(C6_clusters_file,header=T)
rownames(C6_clusters) <- C6_clusters$chrom
C6_clusters$juncs <- vapply(rownames(C6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C6_clusters_psi <- C6_clusters[rownames(C6_clusters_sig),]

C7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C7_perind.counts.gz"
C7_clusters <- read.table(C7_clusters_file,header=T)
rownames(C7_clusters) <- C7_clusters$chrom
C7_clusters$juncs <- vapply(rownames(C7_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C7_clusters_psi <- C7_clusters[rownames(C7_clusters_sig),]

P1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P1_perind.counts.gz"
P1_clusters <- read.table(P1_clusters_file,header=T)
rownames(P1_clusters) <- P1_clusters$chrom
P1_clusters$juncs <- vapply(rownames(P1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P1_clusters_psi <- P1_clusters[rownames(P1_clusters_sig),]

P2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P2_perind.counts.gz"
P2_clusters <- read.table(P2_clusters_file,header=T)
rownames(P2_clusters) <- P2_clusters$chrom
P2_clusters$juncs <- vapply(rownames(P2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P2_clusters_psi <- P2_clusters[rownames(P2_clusters_sig),]

P3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P3_perind.counts.gz"
P3_clusters <- read.table(P3_clusters_file,header=T)
rownames(P3_clusters) <- P3_clusters$chrom
P3_clusters$juncs <- vapply(rownames(P3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P3_clusters_psi <- P3_clusters[rownames(P3_clusters_sig),]

P5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P5_perind.counts.gz"
P5_clusters <- read.table(P5_clusters_file,header=T)
rownames(P5_clusters) <- P5_clusters$chrom
P5_clusters$juncs <- vapply(rownames(P5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P5_clusters_psi <- P5_clusters[rownames(P5_clusters_sig),]

P6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P6_perind.counts.gz"
P6_clusters <- read.table(P6_clusters_file,header=T)
rownames(P6_clusters) <- P6_clusters$chrom
P6_clusters$juncs <- vapply(rownames(P6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P6_clusters_psi <- P6_clusters[rownames(P6_clusters_sig),]

P7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P7_perind.counts.gz"
P7_clusters <- read.table(P7_clusters_file,header=T)
rownames(P7_clusters) <- P7_clusters$chrom
P7_clusters$juncs <- vapply(rownames(P7_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P7_clusters_psi <- P7_clusters[rownames(P7_clusters_sig),]

juncs_all <- unique(c(C1_clusters$juncs,C2_clusters$juncs,
           C3_clusters$juncs,C5_clusters$juncs,
           C6_clusters$juncs,C7_clusters$juncs,
           P1_clusters$juncs,P2_clusters$juncs,
           P3_clusters$juncs,P5_clusters$juncs,
           P6_clusters$juncs,P7_clusters$juncs))

```

```{r}

all_sample_psi <- data.frame(juncs_all)
rownames(all_sample_psi) <- juncs_all
all_sample_psi$C1 <- NA
all_sample_psi[C1_clusters$juncs,"C1"]<-C1_clusters$C1
all_sample_psi[C1_clusters$juncs,"U1"]<-C1_clusters$U1
all_sample_psi[C1_clusters$juncs,"U2"]<-C1_clusters$U2
all_sample_psi[C1_clusters$juncs,"U3"]<-C1_clusters$U3
all_sample_psi$C2 <- NA
all_sample_psi[C2_clusters$juncs,"C2"]<-C2_clusters$C2
all_sample_psi[C2_clusters$juncs,"U1"]<-C2_clusters$U1
all_sample_psi[C2_clusters$juncs,"U2"]<-C2_clusters$U2
all_sample_psi[C2_clusters$juncs,"U3"]<-C2_clusters$U3
all_sample_psi$C3 <- NA
all_sample_psi[C3_clusters$juncs,"C3"]<-C3_clusters$C3
all_sample_psi[C3_clusters$juncs,"U1"]<-C3_clusters$U1
all_sample_psi[C3_clusters$juncs,"U2"]<-C3_clusters$U2
all_sample_psi[C3_clusters$juncs,"U3"]<-C3_clusters$U3
all_sample_psi$C5 <- NA
all_sample_psi[C5_clusters$juncs,"C5"]<-C5_clusters$C5
all_sample_psi[C5_clusters$juncs,"U1"]<-C5_clusters$U1
all_sample_psi[C5_clusters$juncs,"U2"]<-C5_clusters$U2
all_sample_psi[C5_clusters$juncs,"U3"]<-C5_clusters$U3
all_sample_psi$C6 <- NA
all_sample_psi[C6_clusters$juncs,"C6"]<-C6_clusters$C6
all_sample_psi[C6_clusters$juncs,"U1"]<-C6_clusters$U1
all_sample_psi[C6_clusters$juncs,"U2"]<-C6_clusters$U2
all_sample_psi[C6_clusters$juncs,"U3"]<-C6_clusters$U3
all_sample_psi$C7 <- NA
all_sample_psi[C7_clusters$juncs,"C7"]<-C7_clusters$C7
all_sample_psi[C7_clusters$juncs,"U1"]<-C7_clusters$U1
all_sample_psi[C7_clusters$juncs,"U2"]<-C7_clusters$U2
all_sample_psi[C7_clusters$juncs,"U3"]<-C7_clusters$U3
all_sample_psi$P1 <- NA
all_sample_psi[P1_clusters$juncs,"P1"]<-P1_clusters$P1
all_sample_psi[P1_clusters$juncs,"U1"]<-P1_clusters$U1
all_sample_psi[P1_clusters$juncs,"U2"]<-P1_clusters$U2
all_sample_psi[P1_clusters$juncs,"U3"]<-P1_clusters$U3
all_sample_psi$P2 <- NA
all_sample_psi[P2_clusters$juncs,"P2"]<-P2_clusters$P2
all_sample_psi[P2_clusters$juncs,"U1"]<-P2_clusters$U1
all_sample_psi[P2_clusters$juncs,"U2"]<-P2_clusters$U2
all_sample_psi[P2_clusters$juncs,"U3"]<-P2_clusters$U3
all_sample_psi$P3 <- NA
all_sample_psi[P3_clusters$juncs,"P3"]<-P3_clusters$P3
all_sample_psi[P3_clusters$juncs,"U1"]<-P3_clusters$U1
all_sample_psi[P3_clusters$juncs,"U2"]<-P3_clusters$U2
all_sample_psi[P3_clusters$juncs,"U3"]<-P3_clusters$U3
all_sample_psi$P5 <- NA
all_sample_psi[P5_clusters$juncs,"P5"]<-P5_clusters$P5
all_sample_psi[P5_clusters$juncs,"U1"]<-P5_clusters$U1
all_sample_psi[P5_clusters$juncs,"U2"]<-P5_clusters$U2
all_sample_psi[P5_clusters$juncs,"U3"]<-P5_clusters$U3
all_sample_psi$P6 <- NA
all_sample_psi[P6_clusters$juncs,"P6"]<-P6_clusters$P6
all_sample_psi[P6_clusters$juncs,"U1"]<-P6_clusters$U1
all_sample_psi[P6_clusters$juncs,"U2"]<-P6_clusters$U2
all_sample_psi[P6_clusters$juncs,"U3"]<-P6_clusters$U3
all_sample_psi$P7 <- NA
all_sample_psi[P7_clusters$juncs,"P7"]<-P7_clusters$P7
all_sample_psi[P7_clusters$juncs,"U1"]<-P7_clusters$U1
all_sample_psi[P7_clusters$juncs,"U2"]<-P7_clusters$U2
all_sample_psi[P7_clusters$juncs,"U3"]<-P7_clusters$U3
all_sample_psi<-all_sample_psi[juncs_sig,seq(2,ncol(all_sample_psi))]

```

Configuring psi matrix to be numeric

```{r}

cols <- colnames(all_sample_psi)
for (col in cols){
  all_sample_psi[,col]<-vapply(all_sample_psi[,col],function(val){
    if (is.na(val)){
      return(NA)
    }
    frac<-strsplit(val,"/")[[1]]
    frac<-as.numeric(frac)
    if (frac[1]==0){
      return(0)
    }
    frac <- frac[1]/frac[2]
  },numeric(1))
}

```

Saving psi and pval matrices

```{r}

write.table(all_sample_psi,
            file="/media/theron/My_Passport/Ali_data/analysis/all_sample_psi.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)
write.table(all_sample_pvals,
            file="/media/theron/My_Passport/Ali_data/analysis/all_sample_pval.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)

juncs_sig_df <- data.frame(matrix(unlist(strsplit(juncs_sig,":")),nrow=length(juncs_sig),ncol=4,byrow=T))
colnames(juncs_sig_df)<-c("chrom","start","end","strand")

write.table(juncs_sig_df,
            file="/media/theron/My_Passport/Ali_data/analysis/juncs_sig.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)
saveRDS(juncs_sig_df,
        file="/media/theron/My_Passport/Ali_data/analysis/juncs_sig.rds")

juncs_all_df <- data.frame(matrix(unlist(strsplit(juncs_all,":")),nrow=length(juncs_all),ncol=4,byrow=T))
colnames(juncs_all_df)<-c("chrom","start","end","strand")

write.table(juncs_all_df,
            file="/media/theron/My_Passport/Ali_data/analysis/juncs_all.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)

```

# Exploring outlier splice junctions Combo vs PD1 and PD1 vs Combo

## Filtering for significant junctions per sample

```{r}

C1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C1P_pVals.txt"
C1_clusters <- read.table(C1_clusters_file,header=T)
C1_clusters$juncs <- vapply(rownames(C1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C1_clusters_sig <- C1_clusters %>% dplyr::filter(C1 <= 0.05)


C2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C2P_pVals.txt"
C2_clusters <- read.table(C2_clusters_file,header=T)
C2_clusters$juncs <- vapply(rownames(C2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C2_clusters_sig <- C2_clusters %>% dplyr::filter(C2 <= 0.05)

C3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C3P_pVals.txt"
C3_clusters <- read.table(C3_clusters_file,header=T)
C3_clusters$juncs <- vapply(rownames(C3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C3_clusters_sig <- C3_clusters %>% dplyr::filter(C3 <= 0.05)

C5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C5P_pVals.txt"
C5_clusters <- read.table(C5_clusters_file,header=T)
C5_clusters$juncs <- vapply(rownames(C5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C5_clusters_sig <- C5_clusters %>% dplyr::filter(C5 <= 0.05)

C6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C6P_pVals.txt"
C6_clusters <- read.table(C6_clusters_file,header=T)
C6_clusters$juncs <- vapply(rownames(C6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
C6_clusters_sig <- C6_clusters %>% dplyr::filter(C6 <= 0.05)

C7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C7P_pVals.txt"
C7_clusters <- read.table(C7_clusters_file,header=T)
C7_clusters_sig <- C7_clusters %>% dplyr::filter(C7 <= 0.05)
C7_clusters_sig$juncs <- vapply(rownames(C7_clusters_sig),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))

P1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P1C_pVals.txt"
P1_clusters <- read.table(P1_clusters_file,header=T)
P1_clusters$juncs <- vapply(rownames(P1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
P1_clusters_sig <- P1_clusters %>% dplyr::filter(P1 <= 0.05)

P2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P2C_pVals.txt"
P2_clusters <- read.table(P2_clusters_file,header=T)
P2_clusters$juncs <- vapply(rownames(P2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
P2_clusters_sig <- P2_clusters %>% dplyr::filter(P2 <= 0.05)

P3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P3C_pVals.txt"
P3_clusters <- read.table(P3_clusters_file,header=T)
P3_clusters$juncs <- vapply(rownames(P3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
  },character(1))
P3_clusters_sig <- P3_clusters %>% dplyr::filter(P3 <= 0.05)

P5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P5C_pVals.txt"
P5_clusters <- read.table(P5_clusters_file,header=T)
P5_clusters$juncs <- vapply(rownames(P5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P5_clusters_sig <- P5_clusters %>% dplyr::filter(P5 <= 0.05)

P6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P6C_pVals.txt"
P6_clusters <- read.table(P6_clusters_file,header=T)
P6_clusters$juncs <- vapply(rownames(P6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P6_clusters_sig <- P6_clusters %>% dplyr::filter(P6 <= 0.05)

P7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P7C_pVals.txt"
P7_clusters <- read.table(P7_clusters_file,header=T)
P7_clusters$juncs <- vapply(rownames(P7_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P7_clusters_sig <- P7_clusters %>% dplyr::filter(P7 <= 0.05)

juncs_sig <- unique(c(C1_clusters_sig$juncs,C2_clusters_sig$juncs,
           C3_clusters_sig$juncs,C5_clusters_sig$juncs,
           C6_clusters_sig$juncs,C7_clusters_sig$juncs,
           P1_clusters_sig$juncs,P2_clusters_sig$juncs,
           P3_clusters_sig$juncs,P5_clusters_sig$juncs,
           P6_clusters_sig$juncs,P7_clusters_sig$juncs))
juncs_all <- unique(c(C1_clusters$juncs,C2_clusters$juncs,
           C3_clusters$juncs,C5_clusters$juncs,
           C6_clusters$juncs,C7_clusters$juncs,
           P1_clusters$juncs,P2_clusters$juncs,
           P3_clusters$juncs,P5_clusters$juncs,
           P6_clusters$juncs,P7_clusters$juncs))

```

## Combining the outlier splicing junctions for each type together

```{r}

all_sample_pvals <- data.frame(juncs_all)
rownames(all_sample_pvals) <- juncs_all
all_sample_pvals$C1 <- NA
all_sample_pvals[C1_clusters$juncs,"C1"]<-C1_clusters$C1
all_sample_pvals$C2 <- NA
all_sample_pvals[C2_clusters$juncs,"C2"]<-C2_clusters$C2
all_sample_pvals$C3 <- NA
all_sample_pvals[C3_clusters$juncs,"C3"]<-C3_clusters$C3
all_sample_pvals$C5 <- NA
all_sample_pvals[C5_clusters$juncs,"C5"]<-C5_clusters$C5
all_sample_pvals$C6 <- NA
all_sample_pvals[C6_clusters$juncs,"C6"]<-C6_clusters$C6
all_sample_pvals$C7 <- NA
all_sample_pvals[C7_clusters$juncs,"C7"]<-C7_clusters$C7
all_sample_pvals$P1 <- NA
all_sample_pvals[P1_clusters$juncs,"P1"]<-P1_clusters$P1
all_sample_pvals$P2 <- NA
all_sample_pvals[P2_clusters$juncs,"P2"]<-P2_clusters$P2
all_sample_pvals$P3 <- NA
all_sample_pvals[P3_clusters$juncs,"P3"]<-P3_clusters$P3
all_sample_pvals$P5 <- NA
all_sample_pvals[P5_clusters$juncs,"P5"]<-P5_clusters$P5
all_sample_pvals$P6 <- NA
all_sample_pvals[P6_clusters$juncs,"P6"]<-P6_clusters$P6
all_sample_pvals$P7 <- NA
all_sample_pvals[P7_clusters$juncs,"P7"]<-P7_clusters$P7
all_sample_pvals<-all_sample_pvals[juncs_sig,seq(2,ncol(all_sample_pvals))]

```

## Using all significant junctions, extracting psi per leafcutter cluster

```{r}

C1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C1P_perind.counts.gz"
C1_clusters <- read.table(C1_clusters_file,header=T)
rownames(C1_clusters) <- C1_clusters$chrom
C1_clusters$juncs <- vapply(rownames(C1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C1_clusters_psi <- C1_clusters[rownames(C1_clusters_sig),]

C2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C2P_perind.counts.gz"
C2_clusters <- read.table(C2_clusters_file,header=T)
rownames(C2_clusters) <- C2_clusters$chrom
C2_clusters$juncs <- vapply(rownames(C2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C2_clusters_psi <- C2_clusters[rownames(C2_clusters_sig),]

C3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C3P_perind.counts.gz"
C3_clusters <- read.table(C3_clusters_file,header=T)
rownames(C3_clusters) <- C3_clusters$chrom
C3_clusters$juncs <- vapply(rownames(C3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C3_clusters_psi <- C3_clusters[rownames(C3_clusters_sig),]

C5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C5P_perind.counts.gz"
C5_clusters <- read.table(C5_clusters_file,header=T)
rownames(C5_clusters) <- C5_clusters$chrom
C5_clusters$juncs <- vapply(rownames(C5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C5_clusters_psi <- C5_clusters[rownames(C5_clusters_sig),]

C6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C6P_perind.counts.gz"
C6_clusters <- read.table(C6_clusters_file,header=T)
rownames(C6_clusters) <- C6_clusters$chrom
C6_clusters$juncs <- vapply(rownames(C6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C6_clusters_psi <- C6_clusters[rownames(C6_clusters_sig),]

C7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/C7P_perind.counts.gz"
C7_clusters <- read.table(C7_clusters_file,header=T)
rownames(C7_clusters) <- C7_clusters$chrom
C7_clusters$juncs <- vapply(rownames(C7_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
C7_clusters_psi <- C7_clusters[rownames(C7_clusters_sig),]

P1_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P1C_perind.counts.gz"
P1_clusters <- read.table(P1_clusters_file,header=T)
rownames(P1_clusters) <- P1_clusters$chrom
P1_clusters$juncs <- vapply(rownames(P1_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P1_clusters_psi <- P1_clusters[rownames(P1_clusters_sig),]

P2_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P2C_perind.counts.gz"
P2_clusters <- read.table(P2_clusters_file,header=T)
rownames(P2_clusters) <- P2_clusters$chrom
P2_clusters$juncs <- vapply(rownames(P2_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P2_clusters_psi <- P2_clusters[rownames(P2_clusters_sig),]

P3_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P3C_perind.counts.gz"
P3_clusters <- read.table(P3_clusters_file,header=T)
rownames(P3_clusters) <- P3_clusters$chrom
P3_clusters$juncs <- vapply(rownames(P3_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P3_clusters_psi <- P3_clusters[rownames(P3_clusters_sig),]

P5_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P5C_perind.counts.gz"
P5_clusters <- read.table(P5_clusters_file,header=T)
rownames(P5_clusters) <- P5_clusters$chrom
P5_clusters$juncs <- vapply(rownames(P5_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P5_clusters_psi <- P5_clusters[rownames(P5_clusters_sig),]

P6_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P6C_perind.counts.gz"
P6_clusters <- read.table(P6_clusters_file,header=T)
rownames(P6_clusters) <- P6_clusters$chrom
P6_clusters$juncs <- vapply(rownames(P6_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P6_clusters_psi <- P6_clusters[rownames(P6_clusters_sig),]

P7_clusters_file <- "/media/theron/My_Passport/Ali_data/analysis/P7C_perind.counts.gz"
P7_clusters <- read.table(P7_clusters_file,header=T)
rownames(P7_clusters) <- P7_clusters$chrom
P7_clusters$juncs <- vapply(rownames(P7_clusters),function(val){
  all_info <- strsplit(val,":")[[1]]
  strand <- strsplit(all_info[4],"_")[[1]][3]
  paste(c(all_info[seq(3)],strand),collapse=":")
},character(1))
P7_clusters_psi <- P7_clusters[rownames(P7_clusters_sig),]

juncs_all <- unique(c(C1_clusters$juncs,C2_clusters$juncs,
           C3_clusters$juncs,C5_clusters$juncs,
           C6_clusters$juncs,C7_clusters$juncs,
           P1_clusters$juncs,P2_clusters$juncs,
           P3_clusters$juncs,P5_clusters$juncs,
           P6_clusters$juncs,P7_clusters$juncs))

```

```{r}

all_sample_psi <- data.frame(juncs_all)
rownames(all_sample_psi) <- juncs_all
all_sample_psi$C1 <- NA
all_sample_psi[C1_clusters$juncs,"C1"]<-C1_clusters$C1

all_sample_psi$C2 <- NA
all_sample_psi[C2_clusters$juncs,"C2"]<-C2_clusters$C2

all_sample_psi$C3 <- NA
all_sample_psi[C3_clusters$juncs,"C3"]<-C3_clusters$C3

all_sample_psi$C5 <- NA
all_sample_psi[C5_clusters$juncs,"C5"]<-C5_clusters$C5

all_sample_psi$C6 <- NA
all_sample_psi[C6_clusters$juncs,"C6"]<-C6_clusters$C6

all_sample_psi$C7 <- NA
all_sample_psi[C7_clusters$juncs,"C7"]<-C7_clusters$C7

all_sample_psi$P1 <- NA
all_sample_psi[P1_clusters$juncs,"P1"]<-P1_clusters$P1

all_sample_psi$P2 <- NA
all_sample_psi[P2_clusters$juncs,"P2"]<-P2_clusters$P2

all_sample_psi$P3 <- NA
all_sample_psi[P3_clusters$juncs,"P3"]<-P3_clusters$P3

all_sample_psi$P5 <- NA
all_sample_psi[P5_clusters$juncs,"P5"]<-P5_clusters$P5

all_sample_psi$P6 <- NA
all_sample_psi[P6_clusters$juncs,"P6"]<-P6_clusters$P6

all_sample_psi$P7 <- NA
all_sample_psi[P7_clusters$juncs,"P7"]<-P7_clusters$P7
all_sample_psi<-all_sample_psi[juncs_sig,seq(2,ncol(all_sample_psi))]

```

Normalizing and conglomerating the junction counts per outlier junction

```{r}

C1_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/C1.junc",sep="\t")
C1_juncs$juncs<-sprintf("%s:%s:%s:%s",C1_juncs$V1,C1_juncs$V2,C1_juncs$V3,C1_juncs$V6)
C1_juncs$norm <- (C1_juncs$V5/sum(C1_juncs$V5))*10000
C1_juncs<-vapply(juncs_sig,function(junc){
  a<-which(C1_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(C1_juncs[a,"norm"]))
  }
},numeric(1))
names(C1_juncs)<-juncs_sig
C1_juncs<-data.frame(C1_juncs)
C1_juncs$juncs<-rownames(C1_juncs)
C1_juncs <- C1_juncs %>% dplyr::filter(juncs %in% juncs_sig)

C2_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/C2.junc",sep="\t")
C2_juncs$juncs<-sprintf("%s:%s:%s:%s",C2_juncs$V1,C2_juncs$V2,C2_juncs$V3,C2_juncs$V6)
C2_juncs$norm <- (C2_juncs$V5/sum(C2_juncs$V5))*10000
C2_juncs<-vapply(juncs_sig,function(junc){
  a<-which(C2_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(C2_juncs[a,"norm"]))
  }
},numeric(1))
names(C2_juncs)<-juncs_sig
C2_juncs<-data.frame(C2_juncs)
C2_juncs$juncs<-rownames(C2_juncs)
C2_juncs <- C2_juncs %>% dplyr::filter(juncs %in% juncs_sig)

C3_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/C3.junc",sep="\t")
C3_juncs$juncs<-sprintf("%s:%s:%s:%s",C3_juncs$V1,C3_juncs$V2,C3_juncs$V3,C3_juncs$V6)
C3_juncs$norm <- (C3_juncs$V5/sum(C3_juncs$V5))*10000
C3_juncs<-vapply(juncs_sig,function(junc){
  a<-which(C3_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(C3_juncs[a,"norm"]))
  }
},numeric(1))
names(C3_juncs)<-juncs_sig
C3_juncs<-data.frame(C3_juncs)
C3_juncs$juncs<-rownames(C3_juncs)
C3_juncs <- C3_juncs %>% dplyr::filter(juncs %in% juncs_sig)

C5_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/C5.junc",sep="\t")
C5_juncs$juncs<-sprintf("%s:%s:%s:%s",C5_juncs$V1,C5_juncs$V2,C5_juncs$V3,C5_juncs$V6)
C5_juncs$norm <- (C5_juncs$V5/sum(C5_juncs$V5))*10000
C5_juncs<-vapply(juncs_sig,function(junc){
  a<-which(C5_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(C5_juncs[a,"norm"]))
  }
},numeric(1))
names(C5_juncs)<-juncs_sig
C5_juncs<-data.frame(C5_juncs)
C5_juncs$juncs<-rownames(C5_juncs)
C5_juncs <- C5_juncs %>% dplyr::filter(juncs %in% juncs_sig)

C6_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/C6.junc",sep="\t")
C6_juncs$juncs<-sprintf("%s:%s:%s:%s",C6_juncs$V1,C6_juncs$V2,C6_juncs$V3,C6_juncs$V6)
C6_juncs$norm <- (C6_juncs$V5/sum(C6_juncs$V5))*10000
C6_juncs<-vapply(juncs_sig,function(junc){
  a<-which(C6_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(C6_juncs[a,"norm"]))
  }
},numeric(1))
names(C6_juncs)<-juncs_sig
C6_juncs<-data.frame(C6_juncs)
C6_juncs$juncs<-rownames(C6_juncs)
C6_juncs <- C6_juncs %>% dplyr::filter(juncs %in% juncs_sig)

C7_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/C7.junc",sep="\t")
C7_juncs$juncs<-sprintf("%s:%s:%s:%s",C7_juncs$V1,C7_juncs$V2,C7_juncs$V3,C7_juncs$V6)
C7_juncs$norm <- (C7_juncs$V5/sum(C7_juncs$V5))*10000
C7_juncs<-vapply(juncs_sig,function(junc){
  a<-which(C7_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(C7_juncs[a,"norm"]))
  }
},numeric(1))
names(C7_juncs)<-juncs_sig
C7_juncs<-data.frame(C7_juncs)
C7_juncs$juncs<-rownames(C7_juncs)
C7_juncs <- C7_juncs %>% dplyr::filter(juncs %in% juncs_sig)

P1_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/P1.junc",sep="\t")
P1_juncs$juncs<-sprintf("%s:%s:%s:%s",P1_juncs$V1,P1_juncs$V2,P1_juncs$V3,P1_juncs$V6)
P1_juncs$norm <- (P1_juncs$V5/sum(P1_juncs$V5))*10000
P1_juncs<-vapply(juncs_sig,function(junc){
  a<-which(P1_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(P1_juncs[a,"norm"]))
  }
},numeric(1))
names(P1_juncs)<-juncs_sig
P1_juncs<-data.frame(P1_juncs)
P1_juncs$juncs<-rownames(P1_juncs)
P1_juncs <- P1_juncs %>% dplyr::filter(juncs %in% juncs_sig)

P2_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/P2.junc",sep="\t")
P2_juncs$juncs<-sprintf("%s:%s:%s:%s",P2_juncs$V1,P2_juncs$V2,P2_juncs$V3,P2_juncs$V6)
P2_juncs$norm <- (P2_juncs$V5/sum(P2_juncs$V5))*10000
P2_juncs<-vapply(juncs_sig,function(junc){
  a<-which(P2_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(P2_juncs[a,"norm"]))
  }
},numeric(1))
names(P2_juncs)<-juncs_sig
P2_juncs<-data.frame(P2_juncs)
P2_juncs$juncs<-rownames(P2_juncs)
P2_juncs <- P2_juncs %>% dplyr::filter(juncs %in% juncs_sig)

P3_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/P3.junc",sep="\t")
P3_juncs$juncs<-sprintf("%s:%s:%s:%s",P3_juncs$V1,P3_juncs$V2,P3_juncs$V3,P3_juncs$V6)
P3_juncs$norm <- (P3_juncs$V5/sum(P3_juncs$V5))*10000
P3_juncs<-vapply(juncs_sig,function(junc){
  a<-which(P3_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(P3_juncs[a,"norm"]))
  }
},numeric(1))
names(P3_juncs)<-juncs_sig
P3_juncs<-data.frame(P3_juncs)
P3_juncs$juncs<-rownames(P3_juncs)
P3_juncs <- P3_juncs %>% dplyr::filter(juncs %in% juncs_sig)

P5_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/P5.junc",sep="\t")
P5_juncs$juncs<-sprintf("%s:%s:%s:%s",P5_juncs$V1,P5_juncs$V2,P5_juncs$V3,P5_juncs$V6)
P5_juncs$norm <- (P5_juncs$V5/sum(P5_juncs$V5))*10000
P5_juncs<-vapply(juncs_sig,function(junc){
  a<-which(P5_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(P5_juncs[a,"norm"]))
  }
},numeric(1))
names(P5_juncs)<-juncs_sig
P5_juncs<-data.frame(P5_juncs)
P5_juncs$juncs<-rownames(P5_juncs)
P5_juncs <- P5_juncs %>% dplyr::filter(juncs %in% juncs_sig)

P6_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/P6.junc",sep="\t")
P6_juncs$juncs<-sprintf("%s:%s:%s:%s",P6_juncs$V1,P6_juncs$V2,P6_juncs$V3,P6_juncs$V6)
P6_juncs$norm <- (P6_juncs$V5/sum(P6_juncs$V5))*10000
P6_juncs<-vapply(juncs_sig,function(junc){
  a<-which(P6_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(P6_juncs[a,"norm"]))
  }
},numeric(1))
names(P6_juncs)<-juncs_sig
P6_juncs<-data.frame(P6_juncs)
P6_juncs$juncs<-rownames(P6_juncs)
P6_juncs <- P6_juncs %>% dplyr::filter(juncs %in% juncs_sig)

P7_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/P7.junc",sep="\t")
P7_juncs$juncs<-sprintf("%s:%s:%s:%s",P7_juncs$V1,P7_juncs$V2,P7_juncs$V3,P7_juncs$V6)
P7_juncs$norm <- (P7_juncs$V5/sum(P7_juncs$V5))*10000
P7_juncs<-vapply(juncs_sig,function(junc){
  a<-which(P7_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(P7_juncs[a,"norm"]))
  }
},numeric(1))
names(P7_juncs)<-juncs_sig
P7_juncs<-data.frame(P7_juncs)
P7_juncs$juncs<-rownames(P7_juncs)
P7_juncs <- P7_juncs %>% dplyr::filter(juncs %in% juncs_sig)

U1_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/U1.junc",sep="\t")
U1_juncs$juncs<-sprintf("%s:%s:%s:%s",U1_juncs$V1,U1_juncs$V2,U1_juncs$V3,U1_juncs$V6)
U1_juncs$norm <- (U1_juncs$V5/sum(U1_juncs$V5))*10000
U1_juncs<-vapply(juncs_sig,function(junc){
  a<-which(U1_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(U1_juncs[a,"norm"]))
  }
},numeric(1))
names(U1_juncs)<-juncs_sig
U1_juncs<-data.frame(U1_juncs)
U1_juncs$juncs<-rownames(U1_juncs)
U1_juncs <- U1_juncs %>% dplyr::filter(juncs %in% juncs_sig)

U2_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/U2.junc",sep="\t")
U2_juncs$juncs<-sprintf("%s:%s:%s:%s",U2_juncs$V1,U2_juncs$V2,U2_juncs$V3,U2_juncs$V6)
U2_juncs$norm <- (U2_juncs$V5/sum(U2_juncs$V5))*10000
U2_juncs<-vapply(juncs_sig,function(junc){
  a<-which(U2_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(U2_juncs[a,"norm"]))
  }
},numeric(1))
names(U2_juncs)<-juncs_sig
U2_juncs<-data.frame(U2_juncs)
U2_juncs$juncs<-rownames(U2_juncs)
U2_juncs <- U2_juncs %>% dplyr::filter(juncs %in% juncs_sig)

U3_juncs <- read.table("/media/theron/My_Passport/Ali_data/analysis/U3.junc",sep="\t")
U3_juncs$juncs<-sprintf("%s:%s:%s:%s",U3_juncs$V1,U3_juncs$V2,U3_juncs$V3,U3_juncs$V6)
U3_juncs$norm <- (U3_juncs$V5/sum(U3_juncs$V5))*10000
U3_juncs<-vapply(juncs_sig,function(junc){
  a<-which(U3_juncs$juncs==junc)
  if(length(a)==0){
    return(0)
  } else {
    return(as.numeric(U3_juncs[a,"norm"]))
  }
},numeric(1))
names(U3_juncs)<-juncs_sig
U3_juncs<-data.frame(U3_juncs)
U3_juncs$juncs<-rownames(U3_juncs)
U3_juncs <- U3_juncs %>% dplyr::filter(juncs %in% juncs_sig)

all_sample_counts_norm <- cbind(C1_juncs$C1_juncs,
                                C2_juncs$C2_juncs,
                                C3_juncs$C3_juncs,
                                C5_juncs$C5_juncs,
                                C6_juncs$C6_juncs,
                                C7_juncs$C7_juncs,
                                P1_juncs$P1_juncs,
                                P2_juncs$P2_juncs,
                                P3_juncs$P3_juncs,
                                P5_juncs$P5_juncs,
                                P6_juncs$P6_juncs,
                                P7_juncs$P7_juncs,
                                U1_juncs$U1_juncs,
                                U2_juncs$U2_juncs,
                                U3_juncs$U3_juncs,
                                data.frame(juncs_sig))
colnames(all_sample_counts_norm)<-c("C1_norm","C2_norm","C3_norm","C5_norm","C6_norm","C7_norm",
                                "P1_norm","P2_norm","P3_norm","P5_norm","P6_norm","P7_norm",
                                "U1_norm","U2_norm","U3_norm","juncs")

```


Configuring psi matrix to be numeric

```{r}

cols <- colnames(all_sample_psi)
for (col in cols){
  all_sample_psi[,col]<-vapply(all_sample_psi[,col],function(val){
    if (is.na(val)){
      return(NA)
    }
    frac<-strsplit(val,"/")[[1]]
    frac<-as.numeric(frac)
    if (frac[1]==0){
      return(0)
    }
    frac <- frac[1]/frac[2]
  },numeric(1))
}

```



Saving psi and pval matrices

```{r}

write.table(all_sample_psi,
            file="/media/theron/My_Passport/Ali_data/analysis/all_sample_psi_CP_PC.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)
write.table(all_sample_pvals,
            file="/media/theron/My_Passport/Ali_data/analysis/all_sample_pval_CP_PC.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)
write.table(all_sample_counts_norm,
            file="/media/theron/My_Passport/Ali_data/analysis/all_sample_counts_norm_CP_PC.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)

juncs_sig_df <- data.frame(matrix(unlist(strsplit(juncs_sig,":")),nrow=length(juncs_sig),ncol=4,byrow=T))
colnames(juncs_sig_df)<-c("chrom","start","end","strand")

write.table(juncs_sig_df,
            file="/media/theron/My_Passport/Ali_data/analysis/juncs_sig_CP_PC.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)
saveRDS(juncs_sig_df,
        file="/media/theron/My_Passport/Ali_data/analysis/juncs_sig_CP_PC.rds")

juncs_all_df <- data.frame(matrix(unlist(strsplit(juncs_all,":")),nrow=length(juncs_all),ncol=4,byrow=T))
colnames(juncs_all_df)<-c("chrom","start","end","strand")

write.table(juncs_all_df,
            file="/media/theron/My_Passport/Ali_data/analysis/juncs_all_CP_PC.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)

```

# splicemutr junction annotations run on juncs_sig_df

```{r}

txdb_file<-"/media/theron/My_Passport/reference_genomes/GTF_GFF/ENSEMBL/Mus_musculus.GRCm38.102.chr.sqlite"
txdb<-loadDb(txdb_file) # making the txdb from gtf

introns_by_tx<-data.frame(unlist(intronsByTranscript(txdb,use.names=T)))
juncs_test<-sprintf("%s:%s:%s:%s",introns_by_tx$seqnames,introns_by_tx$start-1,introns_by_tx$end+1,introns_by_tx$strand)
introns_by_tx$juncs <- juncs_test
C1_SJ<-read.table("/media/theron/My_Passport/Ali_data/analysis/C1SJ.out.tab")
C1_SJ_strand <- vapply(C1_SJ$V4,function(val){
  if (val == 0){
    return("*")
  } else if (val == 1){
    return("+")
  } else if (val == 2){
    return("-")
  }
},character(1))
juncs<-sprintf("%s:%s:%s:%s",C1_SJ$V1,C1_SJ$V2,C1_SJ$V3,C1_SJ_strand)

annotated_outlier_junctions<-juncs_all %in% introns_by_tx$juncs
table(annotated_outlier_junctions)

```

# immunogenicity 

## missense mutation immunogenicity

```{r}

maf_file <- "/media/theron/My_Passport/Ali_data/WES Data for 4T1MIS/MB01JHU503/MB01JHU503_000_analysis/MAF/DNA_4TIMSI_haplotypecaller.maf"
ali_maf = read.maf(maf_file)
ali_maf_df <- data.frame(ali_maf@data)
ali_maf_df_miss <- ali_maf_df %>% dplyr::filter(Variant_Type=="SNP" & Variant_Classification=="Missense_Mutation")

```

## extracting transcript information 

```{r}

transcripts <- lapply(ali_maf_df_miss$all_effects,function(val){
  val_split <- strsplit(val,",")[[1]]
  val_split[str_detect(val_split,"ENSMUST")]
})
refseq_transcripts <- lapply(ali_maf_df_miss$all_effects,function(val){
  val_split <- strsplit(val,",")[[1]]
  loc <- which(str_detect(val_split,"ENSMUST"))
  unlist(lapply(strsplit(val_split[loc+1],";"),function(val){return(val[1])}))
})

ens_refseq<-data.frame(unlist(transcripts),unlist(refseq_transcripts))
colnames(ens_refseq)<-c("ensembl","refseq")
ens_refseq<-unique(ens_refseq)

```

```{r,eval=FALSE}

source("/media/theron/My_Passport/splicemute/R/functions.R")
locate_mutation_in_cds <- function(cds_tx_sort,mutation_chr,
                                   mutation_start,mutation_end){
  width <- running_sum(cds_tx_sort$width)
  for (i in seq(nrow(cds_tx_sort))){
    if(mutation_end <= cds_tx_sort[i,"end"] & mutation_end >= cds_tx_sort[i,"start"]){
      return(width[i] - (cds_tx_sort[i,"end"]-mutation_end))
    }
  }
  return(-1)
}

extract_portion <- function(trans_str,mut_loc_prot){
  trans_str_split <- strsplit(trans_str,"")[[1]]
  trans_str_split[mut_loc_prot] <- tolower(trans_str_split[mut_loc_prot])
  start <- mut_loc_prot - 8
  if (start < 1){
    start<-1
  }
  end <- mut_loc_prot + 8
  if (end > nchar(trans_str)){
    end <- nchar(trans_str)
  }
  return(paste(trans_str_split[seq(start,end)],collapse=""))
}

conjugate <- function(nuc){
  if (nuc == "A"){
    return("T")
  } else if (nuc == "T"){
    return("A")
  } else if (nuc == "G"){
    return("C")
  } else if (nuc == "C"){
    return("G")
  }
}

BSgenome <- BSgenome.Mmusculus.GENCODE.GRCm38.102
txdb<-loadDb("/media/theron/My_Passport/reference_genomes/GTF_GFF/ENSEMBL/Mus_musculus.GRCm38.102.chr.sqlite")
cds_by_tx<-cdsBy(txdb,by="tx",use.names=T)
protein_coding_txs <- names(cds_by_tx)
tots<-nrow(ali_maf_df_miss)
ali_maf_dat_muts <- as.data.frame(t(vapply(seq(tots),function(i){
  if (i %% 100 == 0){print(sprintf("%d out of%d",i,tots))}
  txs <- transcripts[[i]]
  tx_record <- c()
  mut_loc <- vapply(txs,function(val){
    tx_record <<-c(tx_record,val)
    if (val %in% protein_coding_txs){
      cds_tx <- cds_by_tx[[val]]
      cds_tx_sort <- as.data.frame(sort(cds_tx))
      mutation_chr <- ali_maf_df_miss$Chromosome[i]
      mutation_start <- ali_maf_df_miss$Start_Position[i]
      mutation_end <- ali_maf_df_miss$End_Position[i]
      mutation_strand <- ali_maf_df_miss$Strand[i]
      mutation_allele <- ali_maf_df_miss$Allele[i]
      mutation_allele_norm <- ali_maf_df_miss$Reference_Allele[i]
      mut_loc<-locate_mutation_in_cds(cds_tx_sort,mutation_chr,
                                   mutation_start,mutation_end)
      sequence<-getSeq(BSgenome,sort(cds_tx))
      sequ<-paste(as.character(sequence[1:length(sequence)]), collapse="")
      if(!check_tx(sequ)){return("untrans")}
      if (mut_loc == -1){
        return("outside_cds")
      }
      sequ_split<-strsplit(sequ,"")[[1]]
      if (mutation_strand != cds_tx_sort$strand[1]){
        sequ_split[mut_loc]<-conjugate(mutation_allele)
        sequ_mut <- paste(sequ_split,collapse="")
      } else if (mutation_strand == cds_tx_sort$strand[1]){
        sequ_split[mut_loc]<-mutation_allele
        sequ_mut <- paste(sequ_split,collapse="")
      }
      trans<-translate(DNAStringSet(sequ_mut),no.init.codon = F)
      mut_loc_prot <- floor(mut_loc/3)
      trans_str <- as.character(trans)
      portion <- extract_portion(trans_str,mut_loc_prot)
      return(portion)
    } else {
      return("outside_cds")
    }
  },character(1))
  mut_loc_names <- paste(names(mut_loc),collapse=":")
  mut_loc_vals <- paste(unname(mut_loc),collapse=":")
  return(c(mut_loc_names,mut_loc_vals))
},character(2))))

write.table(ali_maf_dat_muts,
            file="/media/theron/My_Passport/Ali_data/analysis/ali_maf_muts.txt",
            sep="\t",
            quote=F,
            col.names=T,
            row.names=F)
saveRDS(ali_maf_dat_muts,file="/media/theron/My_Passport/Ali_data/analysis/ali_maf_muts.rds")

```

# creating fasta file

```{r,eval=F}

ali_maf_dat_muts <- read.table("/media/theron/My_Passport/Ali_data/analysis/ali_maf_muts.txt",header = T)
sequences<-lapply(seq(nrow(ali_maf_dat_muts)),function(row_val){
  transcripts<-strsplit(ali_maf_dat_muts$V1[row_val],":")[[1]]
  sequences<-strsplit(ali_maf_dat_muts$V2[row_val],":")[[1]]
  keep<-!(sequences %in% c("outside_cds","untrans"))
  if (!any(keep)){return(NA)}
  tx<-transcripts[keep]
  seq<-sequences[keep]
  names(seq)<-sprintf("%s_%d",tx,rep(row_val,length(which(keep))))
  return(seq)
})
sequences<-unlist(sequences)
sequences<-sequences[!is.na(sequences)]
tx_name <- names(sequences)
sequences <- vapply(sequences,function(seq){
  seq<-toupper(seq)
  seq<-str_replace_all(seq,"[*]","")
},character(1))
names(sequences)<-seq(length(tx_name))
sequences<-AAStringSet(sequences)
out_fasta<-"/media/theron/My_Passport/Ali_data/analysis/ali_maf_muts.fa"
writeXStringSet(sequences,out_fasta)
saveRDS(tx_name,file="/media/theron/My_Passport/Ali_data/analysis/tx_names.rds")

```

```{r,eval=F}

breaks<-seq(1,length(sequences),5000)

for (i in seq(length(breaks))){
  if (i == length(breaks)){
    sequences_small<-AAStringSet(sequences[seq(breaks[i],length(sequences))])
    out_fasta<-sprintf("/media/theron/My_Passport/Ali_data/analysis/ali_maf_muts_%d.fa",i)
    writeXStringSet(sequences_small,out_fasta,append=FALSE)
  } else {
    sequences_small<-AAStringSet(sequences[seq(breaks[i],breaks[i+1]-1)])
    out_fasta<-sprintf("/media/theron/My_Passport/Ali_data/analysis/ali_maf_muts_%d.fa",i)
    writeXStringSet(sequences_small,out_fasta,append=FALSE)
  }
}

```

## combining netmhc output for mutations

```{r}

mut1<-read.table("/media/theron/My_Passport/Ali_data/analysis/immunogenicity/mut1_NetMHC.txt",header=T)
mut2<-read.table("/media/theron/My_Passport/Ali_data/analysis/immunogenicity/mut2_NetMHC.txt",header=T)
mut3<-read.table("/media/theron/My_Passport/Ali_data/analysis/immunogenicity/mut3_NetMHC.txt",header=T)
mut4<-read.table("/media/theron/My_Passport/Ali_data/analysis/immunogenicity/mut4_NetMHC.txt",header=T)
mut_imm <- rbind(mut1,mut2,mut3,mut4)
mut_imm_binding <- mut_imm %>% dplyr::filter(N_binders>0)
tx_names<-readRDS("/media/theron/My_Passport/Ali_data/analysis/tx_names.rds")
tx_names<-data.frame(t(vapply(tx_names,function(tx){str_split(tx,"_")[[1]]},character(2))))
mut_imm_binding$tx<-NA
mut_imm_binding$row_val<-NA
mut_imm_binding[,c("tx","row_val")]<-tx_names[mut_imm_binding$ID,c("X1","X2")]

```

## Creating fold change log per transcript and arm

```{r}

isoform_diff_expr <- "/media/theron/My_Passport/Ali_data/HTMBmice_RNAseq_Data/MB01JHU504/MB01JHU504_000_analysis/DESeq2/isoforms"
pd1_vs_combo <- read.table(sprintf("%s/PD1_vs_Combo_isoforms_DESeq2.txt",isoform_diff_expr),header=T)
pd1_vs_combo <- pd1_vs_combo %>% dplyr::filter(PD1_vs_Combo_pvalue <= 0.05)
untreated_vs_combo <- read.table(sprintf("%s/Untreated_vs_Combo_isoforms_DESeq2.txt",isoform_diff_expr),header=T)
untreated_vs_combo <- untreated_vs_combo %>% dplyr::filter(Untreated_vs_Combo_pvalue <= 0.05)
untreated_vs_pd1 <- read.table(sprintf("%s/Untreated_vs_PD1_isoforms_DESeq2.txt",isoform_diff_expr),header=T)
untreated_vs_pd1 <- untreated_vs_pd1 %>% dplyr::filter(Untreated_vs_PD1_pvalue <= 0.05)
diff_data <- data.frame(c(pd1_vs_combo$transcript_id,untreated_vs_combo$transcript_id,untreated_vs_pd1$transcript_id),
                               c(pd1_vs_combo$gene_id,untreated_vs_combo$gene_id,untreated_vs_pd1$gene_id))
colnames(diff_data)<-c("transcript","gene")
diff_dat <- unique(diff_data)

```

## Looking at mutation expression


## Looking at mutation expression per sample

```{r}

RSEM_transcripts <- read.table("/media/theron/My_Passport/Ali_data/HTMBmice_RNAseq_Data/MB01JHU504/MB01JHU504_000_analysis/RSEM/tables/isoforms/isoforms_tpm_all_samples_norm.txt",header=T)
rownames(RSEM_transcripts) <- RSEM_transcripts$transcript_id
RSEM_transcripts<-RSEM_transcripts %>% dplyr::filter(transcript_id %in% diff_dat$transcript)

refseq_val <- vapply(mut_imm_binding$tx,function(ID){
  a <- which(ens_refseq$ensembl==ID)
  if (length(a) == 0){
    return("-1")
  } else {
    refseq_val<-ens_refseq$refseq[a[1]]
    return(substr(refseq_val,1,nchar(refseq_val)-2))
  }
  
},character(1))
N_binders<-mut_imm_binding$N_binders
row_val<-mut_imm_binding$row_val

RSEM_refseq<-cbind(RSEM_transcripts[unname(refseq_val),],N_binders,row_val)

RSEM_refseq_complete <- RSEM_refseq[!is.na(RSEM_refseq$transcript_id),]
C_mut_av <- RSEM_refseq_complete[,seq(3,8)]
C_mut_vals<-vapply(seq(nrow(C_mut_av)),function(row_val){
  mean(as.numeric(C_mut_av[row_val,]),na.rm = T)
},numeric(1))
C_mut_vals_med<-vapply(seq(nrow(C_mut_av)),function(row_val){
  median(as.numeric(C_mut_av[row_val,]),na.rm = T)
},numeric(1))
P_mut_av <- RSEM_refseq_complete[,seq(9,14)]
P_mut_vals<-vapply(seq(nrow(P_mut_av)),function(row_val){
  mean(as.numeric(P_mut_av[row_val,]),na.rm = T)
},numeric(1))
P_mut_vals_med<-vapply(seq(nrow(P_mut_av)),function(row_val){
  median(as.numeric(P_mut_av[row_val,]),na.rm = T)
},numeric(1))
U_mut_av <- RSEM_refseq_complete[,seq(15,17)]
U_mut_vals<-vapply(seq(nrow(U_mut_av)),function(row_val){
  mean(as.numeric(U_mut_av[row_val,]),na.rm = T)
},numeric(1))
U_mut_vals_med<-vapply(seq(nrow(U_mut_av)),function(row_val){
  median(as.numeric(U_mut_av[row_val,]),na.rm = T)
},numeric(1))
RSEM_refseq_average <- data.frame(C_mut_vals,C_mut_vals_med,
                                  P_mut_vals,P_mut_vals_med,
                                  U_mut_vals,U_mut_vals_med,
                                  RSEM_refseq_complete$N_binders,
                                  RSEM_refseq_complete$transcript_id,
                                  RSEM_refseq_complete$gene_id,
                                  RSEM_refseq_complete$row_val)
colnames(RSEM_refseq_average)<-c("C_TPM_AV","C_TPM_MED",
                                 "P_TPM_AV","P_TPM_MED",
                                 "U_TPM_AV","U_TPM_MED",
                                 "N_binders","transcript_id","gene_id",
                                 "row_val")
RSEM_refseq_average_linear <- data.frame(c(RSEM_refseq_average$C_TPM_AV,RSEM_refseq_average$P_TPM_AV,RSEM_refseq_average$U_TPM_AV),
                                         c(RSEM_refseq_average$C_TPM_MED,RSEM_refseq_average$P_TPM_MED,RSEM_refseq_average$U_TPM_MED),
                                         c(rep("combo",nrow(RSEM_refseq_average)),rep("pd1",nrow(RSEM_refseq_average)),rep("untreated",nrow(RSEM_refseq_average))),
                                         rep(RSEM_refseq_average$transcript_id,3),rep(RSEM_refseq_average$gene_id,3),
                                         rep(RSEM_refseq_average$row_val,3),rep(RSEM_refseq_average$N_binders,3))
colnames(RSEM_refseq_average_linear)<-c("TPM_AV","TPM_MED","arm","transcript_id","gene_id","row_val","N_binders")
RSEM_refseq_average_linear$unique_id<-sprintf("%s_%s",RSEM_refseq_average_linear$transcript_id,RSEM_refseq_average_linear$row_val)

my_comparisons <- list( c("combo", "pd1"), c("combo", "untreated"), c("pd1", "untreated") )
ggplot(RSEM_refseq_average_linear,aes(x=arm,y=log10(TPM_AV)))+geom_violin(aes(fill=arm))+
  stat_compare_means(comparisons = my_comparisons)
ggplot(RSEM_refseq_average_linear,aes(x=arm,y=log10(TPM_MED)))+geom_violin(aes(fill=arm))+
  stat_compare_means(comparisons = my_comparisons)

ggplot(RSEM_refseq_average_linear,aes(x=arm,y=log10(TPM_AV),group=unique_id,color=unique_id))+
  geom_point(size=0.5)+geom_line(size=0.1)+
  theme(legend.position = "none")
ggplot(RSEM_refseq_average_linear,aes(x=arm,y=log10(TPM_MED),group=unique_id,color=unique_id))+
  geom_point(size=0.5)+geom_line(size=0.1)+
  theme(legend.position = "none")

ggplot(RSEM_refseq_average_linear,aes(x=unique_id,y=log10(TPM_AV),group=arm,color=arm))+
  geom_point(shape=1)+geom_line()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggplot(RSEM_refseq_average_linear,aes(x=unique_id,y=log10(TPM_MED),group=arm,color=arm))+
  geom_point(shape=1)+geom_line()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

RSEM_refseq_average$unique_id<-sprintf("%s_%s",RSEM_refseq_average$transcript_id,RSEM_refseq_average$row_val)
RSEM_refseq_average$expression_order <- vapply(seq(nrow(RSEM_refseq_average)),function(row_val){
  vals<-RSEM_refseq_average[row_val, c("C_TPM_AV","P_TPM_AV","U_TPM_AV")]
  if (vals$C_TPM_AV < vals$P_TPM_AV & vals$P_TPM_AV < vals$U_TPM_AV){
    return("combo<pd1<untreated")
  } else if (vals$C_TPM_AV < vals$U_TPM_AV & vals$U_TPM_AV < vals$P_TPM_AV) {
    return("combo<untreated<pd1")
  } else if (vals$P_TPM_AV < vals$C_TPM_AV & vals$C_TPM_AV < vals$U_TPM_AV){
    return("pd1<combo<untreated")
  } else if (vals$P_TPM_AV < vals$U_TPM_AV & vals$U_TPM_AV < vals$C_TPM_AV){
    return("pd1<untreated<combo")
  } else if (vals$U_TPM_AV < vals$P_TPM_AV & vals$P_TPM_AV < vals$C_TPM_AV) {
    return("untreated<pd1<combo")
  } else if (vals$U_TPM_AV < vals$C_TPM_AV & vals$C_TPM_AV < vals$P_TPM_AV) {
    return("untreated<combo<pd1")
  } else {
    return("something's equal")
  }
},character(1))
RSEM_refseq_average$expression_order_med <- vapply(seq(nrow(RSEM_refseq_average)),function(row_val){
  vals<-RSEM_refseq_average[row_val, c("C_TPM_MED","P_TPM_MED","U_TPM_MED")]
  if (vals$C_TPM_MED < vals$P_TPM_MED & vals$P_TPM_MED < vals$U_TPM_MED){
    return("combo<pd1<untreated")
  } else if (vals$C_TPM_MED < vals$U_TPM_MED & vals$U_TPM_MED < vals$P_TPM_MED) {
    return("combo<untreated<pd1")
  } else if (vals$P_TPM_MED < vals$C_TPM_MED & vals$C_TPM_MED < vals$U_TPM_MED){
    return("pd1<combo<untreated")
  } else if (vals$P_TPM_MED < vals$U_TPM_MED & vals$U_TPM_MED < vals$C_TPM_MED){
    return("pd1<untreated<combo")
  } else if (vals$U_TPM_MED < vals$P_TPM_MED & vals$P_TPM_MED < vals$C_TPM_MED) {
    return("untreated<pd1<combo")
  } else if (vals$U_TPM_MED < vals$C_TPM_MED & vals$C_TPM_MED < vals$P_TPM_MED) {
    return("untreated<combo<pd1")
  } else {
    return("something's equal")
  }
},character(1))


ggplot(RSEM_refseq_average,aes(x=expression_order,fill=expression_order))+
  geom_bar(aes(y=(..count..)/sum(..count..)))+
  theme(axis.text.x=element_blank())

RSEM_refseq_average_combo_low <- RSEM_refseq_average %>% dplyr::filter(expression_order == "combo<pd1<untreated")
RSEM_refseq_average_combo_high <- RSEM_refseq_average %>% dplyr::filter(expression_order == "untreated<pd1<combo")

ggplot(RSEM_refseq_average_combo_low,aes(x=log2(C_TPM_AV/P_TPM_AV)))+
  geom_histogram()

ggplot(RSEM_refseq_average_combo_high,aes(x=log2(C_TPM_AV/P_TPM_AV)))+
  geom_histogram()

ggplot(RSEM_refseq_average,aes(x=expression_order_med,fill=expression_order_med))+
  geom_bar(aes(y=(..count..)/sum(..count..)))+
  theme(axis.text.x=element_blank())

RSEM_refseq_average_combo_low <- RSEM_refseq_average %>% dplyr::filter(expression_order_med == "combo<pd1<untreated")
RSEM_refseq_average_combo_high <- RSEM_refseq_average %>% dplyr::filter(expression_order_med == "untreated<pd1<combo")

ggplot(RSEM_refseq_average_combo_low,aes(x=log2(C_TPM_MED/P_TPM_MED)))+
  geom_histogram()

ggplot(RSEM_refseq_average_combo_high,aes(x=log2(C_TPM_MED/P_TPM_MED)))+
  geom_histogram()


```

## outlier splicing immunogenicity Combo vs Untreated and PD1 vs Untreated

```{r}

out_splice<-read.table("/media/theron/My_Passport/Ali_data/analysis/immunogenicity/outlier_splicing_NetMHC_results.txt",header=T)
out_splice <- out_splice %>% dplyr::filter(N_binders>0)
splicemutr_dat <- read.table("/media/theron/My_Passport/Ali_data/analysis/formed_transcripts/data_splicemutr.txt",header=T)
juncs <- sprintf("%s:%s:%s:%s",splicemutr_dat$chr,splicemutr_dat$start,splicemutr_dat$end,splicemutr_dat$cluster)
splicemutr_dat$juncs <- juncs

txdb_file<-"/media/theron/My_Passport/reference_genomes/GTF_GFF/ENSEMBL/Mus_musculus.GRCm38.102.chr.sqlite"
txdb<-loadDb(txdb_file) # making the txdb from gtf
introns_by_tx<-data.frame(unlist(intronsByTranscript(txdb,use.names=T)))
juncs_test<-sprintf("%s:%s:%s:%s",introns_by_tx$seqnames,introns_by_tx$start-1,introns_by_tx$end+1,introns_by_tx$strand)
introns_by_tx$juncs <- juncs_test
splicemutr_dat$juncs

annotated_outlier_junctions<-splicemutr_dat$juncs %in% introns_by_tx$juncs
splicemutr_dat$verdict<-"non_ann"
splicemutr_dat$verdict[annotated_outlier_junctions]<-"ann"
table(splicemutr_dat$verdict)

splicemutr_dat_filt <- splicemutr_dat %>% dplyr::filter(!(verdict == "ann" & modified == "changed"))

all_sample_psi<-read.table("/media/theron/My_Passport/Ali_data/analysis/all_sample_psi.txt",header=T)
all_sample_pvals <- read.table("/media/theron/My_Passport/Ali_data/analysis/all_sample_pval.txt",header=T)
juncs_sig <- read.table("/media/theron/My_Passport/Ali_data/analysis/juncs_sig.txt",header=T)
juncs_sig<-sprintf("%s:%s:%s:%s",juncs_sig$chrom,juncs_sig$start,juncs_sig$end,juncs_sig$strand)
rownames(all_sample_psi)<-juncs_sig
  
proteins<-unique(out_splice$ID)
protein_imm_dat<-vapply(proteins,function(prot){
  out_splice_small <- out_splice %>% dplyr::filter(ID==prot)
  sum(out_splice_small$N_binders)
},numeric(1))
prot_imm_dat<-data.frame(proteins,protein_imm_dat)
juncs<-splicemutr_dat$juncs[as.numeric(str_replace_all(proteins,"protein",""))]
prot_imm_dat$juncs<-juncs

C_psi <- all_sample_psi[prot_imm_dat$juncs,c(1,5,6,7,8,9)]
prot_imm_dat$C_psi_av<-vapply(seq(nrow(C_psi)),function(row_val){
  mean(as.numeric(C_psi[row_val,]),na.rm = T)
},numeric(1))
P_psi <- all_sample_psi[prot_imm_dat$juncs,c(10,11,12,13,14,15)]
prot_imm_dat$P_psi_av<-vapply(seq(nrow(P_psi)),function(row_val){
  mean(as.numeric(P_psi[row_val,]),na.rm = T)
},numeric(1))
U_psi <- all_sample_psi[prot_imm_dat$juncs,c(2,3,4)]
prot_imm_dat$U_psi_av<-vapply(seq(nrow(U_psi)),function(row_val){
  mean(as.numeric(U_psi[row_val,]),na.rm = T)
},numeric(1))
prot_imm_dat$P_psi_av[is.nan(prot_imm_dat$P_psi_av)]<-0
prot_imm_dat$C_psi_av[is.nan(prot_imm_dat$C_psi_av)]<-0
prot_imm_dat$U_psi_av[is.nan(prot_imm_dat$U_psi_av)]<-0

prot_imm_dat$psi_order <- vapply(seq(nrow(prot_imm_dat)),function(row_val){
  vals<-prot_imm_dat[row_val,c("P_psi_av","C_psi_av","U_psi_av")]
  if (vals$C_psi_av < vals$P_psi_av & vals$P_psi_av < vals$U_psi_av){
    return("combo<pd1<untreated")
  } else if (vals$C_psi_av < vals$U_psi_av & vals$U_psi_av < vals$P_psi_av){
    return("combo<untreated<pd1")
  } else if (vals$P_psi_av < vals$C_psi_av & vals$C_psi_av < vals$P_psi_av){
    return("pd1<combo<untreated")
  } else if (vals$P_psi_av < vals$U_psi_av & vals$U_psi_av < vals$C_psi_av){
    return("pd1<untreated<combo")
  } else if (vals$U_psi_av < vals$C_psi_av & vals$C_psi_av < vals$P_psi_av){
    return("untreated<combo<pd1")
  } else if (vals$U_psi_av < vals$P_psi_av & vals$P_psi_av < vals$C_psi_av){
    return("untreated<pd1<combo")
  } else {
    return("something's equal")
  }
},character(1))

prot_imm_dat_linear <- data.frame(rep(prot_imm_dat$proteins,3),rep(prot_imm_dat$protein_imm_dat,3),
                                  c(prot_imm_dat$C_psi_av,prot_imm_dat$P_psi_av,prot_imm_dat$U_psi_av),
                                  c(rep("C_psi_av",nrow(prot_imm_dat)),rep("P_psi_av",nrow(prot_imm_dat)),rep("U_psi_av",nrow(prot_imm_dat))))
colnames(prot_imm_dat_linear)<- c("protein","Imm_count","Mean_psi","Treatment")

ggplot(prot_imm_dat_linear,aes(y=Mean_psi,x=protein))+geom_point(aes(color=Treatment))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

my_comparisons <- list( c("C_psi_av", "P_psi_av"), c("C_psi_av", "U_psi_av"), c("P_psi_av", "U_psi_av") )
ggplot(prot_imm_dat_linear,aes(y=Mean_psi,x=Treatment))+geom_violin(aes(fill=Treatment))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  stat_compare_means(comparisons = my_comparisons)

ggplot(prot_imm_dat_linear,aes(y=Mean_psi,x=Treatment,group=protein,color=protein))+
  geom_point()+geom_line()+theme(legend.position = "none")

ggplot(prot_imm_dat_linear,aes(y=Mean_psi,x=log2(Imm_count+1)))+geom_point(aes(color=Treatment))+
  geom_smooth(method = "lm")+
  stat_cor(method = "spearman")

ggplot(prot_imm_dat,aes(x=psi_order,fill=psi_order))+
  geom_bar(aes(y=(..count..)/sum(..count..)))+
  theme(axis.text.x=element_blank())

ggplot(prot_imm_dat,aes(x=psi_order,fill=psi_order))+
  geom_bar()+
  theme(axis.text.x=element_blank())

```

## outlier splicing immunogenicity Combo vs PD1 and PD1 vs Combo

```{r}

out_splice<-read.table("/media/theron/My_Passport/Ali_data/analysis/immunogenicity/outlier_splicing_results_CP_PC_NetMHC.txt",header=T)
out_splice <- out_splice %>% dplyr::filter(N_binders>0)
splicemutr_dat <- read.table("/media/theron/My_Passport/Ali_data/analysis/formed_transcripts_CP_PC/data_splicemutr.txt",header=T)
juncs <- sprintf("%s:%s:%s:%s",splicemutr_dat$chr,splicemutr_dat$start,splicemutr_dat$end,splicemutr_dat$cluster)
splicemutr_dat$juncs <- juncs

txdb_file<-"/media/theron/My_Passport/reference_genomes/GTF_GFF/ENSEMBL/Mus_musculus.GRCm38.102.chr.sqlite"
txdb<-loadDb(txdb_file) # making the txdb from gtf
introns_by_tx<-data.frame(unlist(intronsByTranscript(txdb,use.names=T)))
juncs_test<-sprintf("%s:%s:%s:%s",introns_by_tx$seqnames,introns_by_tx$start-1,introns_by_tx$end+1,introns_by_tx$strand)
introns_by_tx$juncs <- juncs_test
splicemutr_dat$juncs

annotated_outlier_junctions<-splicemutr_dat$juncs %in% introns_by_tx$juncs
splicemutr_dat$verdict<-"non_ann"
splicemutr_dat$verdict[annotated_outlier_junctions]<-"ann"
table(splicemutr_dat$verdict)

splicemutr_dat_filt <- splicemutr_dat %>% dplyr::filter(!(verdict == "ann" & modified == "changed"))

all_sample_psi<-read.table("/media/theron/My_Passport/Ali_data/analysis/all_sample_psi_CP_PC.txt",header=T)
all_sample_pvals <- read.table("/media/theron/My_Passport/Ali_data/analysis/all_sample_pval_CP_PC.txt",header=T)
all_sample_counts_norm <- read.table("/media/theron/My_Passport/Ali_data/analysis/all_sample_counts_norm_CP_PC.txt",header=T)

juncs_sig <- read.table("/media/theron/My_Passport/Ali_data/analysis/juncs_sig_CP_PC.txt",header=T)
juncs_sig<-sprintf("%s:%s:%s:%s",juncs_sig$chrom,juncs_sig$start,juncs_sig$end,juncs_sig$strand)
rownames(all_sample_psi)<-juncs_sig
  
proteins<-unique(out_splice$ID)
protein_imm_dat<-vapply(proteins,function(prot){
  out_splice_small <- out_splice %>% dplyr::filter(ID==prot)
  sum(out_splice_small$N_binders)
},numeric(1))
prot_imm_dat<-data.frame(proteins,protein_imm_dat)
juncs<-splicemutr_dat$juncs[as.numeric(str_replace_all(proteins,"protein",""))]
prot_imm_dat$juncs<-juncs

C_psi <- all_sample_psi[prot_imm_dat$juncs,c(1,2,3,4,5,6)]
prot_imm_dat$C_psi_av<-vapply(seq(nrow(C_psi)),function(row_val){
  mean(as.numeric(C_psi[row_val,]),na.rm = T)
},numeric(1))
prot_imm_dat$C_psi_med<-vapply(seq(nrow(C_psi)),function(row_val){
  median(as.numeric(C_psi[row_val,]),na.rm = T)
},numeric(1))
P_psi <- all_sample_psi[prot_imm_dat$juncs,c(7,8,9,10,11,12)]
prot_imm_dat$P_psi_av<-vapply(seq(nrow(P_psi)),function(row_val){
  median(as.numeric(P_psi[row_val,]),na.rm = T)
},numeric(1))
prot_imm_dat$P_psi_med<-vapply(seq(nrow(P_psi)),function(row_val){
  median(as.numeric(P_psi[row_val,]),na.rm = T)
},numeric(1))

prot_imm_dat$P_psi_av[is.nan(prot_imm_dat$P_psi_av)]<-0
prot_imm_dat$C_psi_av[is.nan(prot_imm_dat$C_psi_av)]<-0
prot_imm_dat$psi_order <- vapply(seq(nrow(prot_imm_dat)),function(row_val){
  vals<-prot_imm_dat[row_val,c("P_psi_av","C_psi_av")]
  if (vals$P_psi_av < vals$C_psi_av){
    return("pd1<combo")
  } else if (vals$P_psi_av > vals$C_psi_av){
    return("combo<pd1")
  } else {
    return("something's equal")
  }
},character(1))

rownames(all_sample_counts_norm)<-all_sample_counts_norm$juncs
C_norm_counts <- all_sample_counts_norm[prot_imm_dat$juncs,c(1,2,3,4,5,6)]
prot_imm_dat$C_norm_counts<-vapply(seq(nrow(C_norm_counts)),function(row_val){
  mean(as.numeric(C_norm_counts[row_val,]),na.rm = T)
},numeric(1))
prot_imm_dat$C_norm_counts_med<-vapply(seq(nrow(C_norm_counts)),function(row_val){
  median(as.numeric(C_norm_counts[row_val,]),na.rm = T)
},numeric(1))
P_norm_counts <- all_sample_counts_norm[prot_imm_dat$juncs,c(7,8,9,10,11,12)]
prot_imm_dat$P_norm_counts<-vapply(seq(nrow(P_norm_counts)),function(row_val){
  mean(as.numeric(P_norm_counts[row_val,]),na.rm = T)
},numeric(1))
prot_imm_dat$P_norm_counts_med<-vapply(seq(nrow(P_norm_counts)),function(row_val){
  median(as.numeric(P_norm_counts[row_val,]),na.rm = T)
},numeric(1))
U_norm_counts <- all_sample_counts_norm[prot_imm_dat$juncs,c(13,14,15)]
prot_imm_dat$U_norm_counts<-vapply(seq(nrow(U_norm_counts)),function(row_val){
  mean(as.numeric(U_norm_counts[row_val,]),na.rm = T)
},numeric(1))
prot_imm_dat$U_norm_counts_med<-vapply(seq(nrow(U_norm_counts)),function(row_val){
  median(as.numeric(U_norm_counts[row_val,]),na.rm = T)
},numeric(1))

prot_imm_dat$P_norm_counts[is.nan(prot_imm_dat$P_norm_counts)]<-0
prot_imm_dat$P_norm_counts_med[is.nan(prot_imm_dat$P_norm_counts)]<-0
prot_imm_dat$C_norm_counts[is.nan(prot_imm_dat$C_norm_counts)]<-0
prot_imm_dat$C_norm_counts_med[is.nan(prot_imm_dat$C_norm_counts)]<-0
prot_imm_dat$U_norm_counts[is.nan(prot_imm_dat$U_norm_counts)]<-0
prot_imm_dat$U_norm_counts_med[is.nan(prot_imm_dat$U_norm_counts)]<-0

prot_imm_dat$counts_order <- vapply(seq(nrow(prot_imm_dat)),function(row_val){
  vals<-prot_imm_dat[row_val,c("P_norm_counts","C_norm_counts","U_norm_counts")]
  if (vals$C_norm_counts < vals$P_norm_counts & vals$C_norm_counts < vals$U_norm_counts){
    return("combo<pd1<untreated")
  } else if (vals$C_norm_counts < vals$U_norm_counts & vals$U_norm_counts < vals$P_norm_counts){
    return("combo<untreated<pd1")
  } else if (vals$P_norm_counts < vals$C_norm_counts & vals$C_norm_counts < vals$P_norm_counts){
    return("pd1<combo<untreated")
  } else if (vals$P_norm_counts < vals$U_norm_counts & vals$U_norm_counts < vals$C_norm_counts){
    return("pd1<untreated<combo")
  } else if (vals$U_norm_counts < vals$C_norm_counts & vals$C_norm_counts < vals$P_norm_counts){
    return("untreated<combo<pd1")
  } else if (vals$U_norm_counts < vals$P_norm_counts & vals$P_norm_counts < vals$C_norm_counts){
    return("untreated<pd1<combo")
  } else {
    return("something's equal")
  }
},character(1))

prot_imm_dat$counts_order_med <- vapply(seq(nrow(prot_imm_dat)),function(row_val){
  vals<-prot_imm_dat[row_val,c("P_norm_counts_med","C_norm_counts_med","U_norm_counts_med")]
  if (vals$C_norm_counts_med < vals$P_norm_counts_med & vals$C_norm_counts_med < vals$U_norm_counts_med){
    return("combo<pd1<untreated")
  } else if (vals$C_norm_counts_med < vals$U_norm_counts_med & vals$U_norm_counts_med < vals$P_norm_counts_med){
    return("combo<untreated<pd1")
  } else if (vals$P_norm_counts_med < vals$C_norm_counts_med & vals$C_norm_counts_med < vals$P_norm_counts_med){
    return("pd1<combo<untreated")
  } else if (vals$P_norm_counts_med < vals$U_norm_counts_med & vals$U_norm_counts_med < vals$C_norm_counts_med){
    return("pd1<untreated<combo")
  } else if (vals$U_norm_counts_med < vals$C_norm_counts_med & vals$C_norm_counts_med < vals$P_norm_counts_med){
    return("untreated<combo<pd1")
  } else if (vals$U_norm_counts_med < vals$P_norm_counts_med & vals$P_norm_counts_med < vals$C_norm_counts_med){
    return("untreated<pd1<combo")
  } else {
    return("something's equal")
  }
},character(1))

prot_imm_dat <- unique(prot_imm_dat[,seq(3,ncol(prot_imm_dat))])

prot_imm_dat_linear_psi <- data.frame(c(prot_imm_dat$C_psi_av,prot_imm_dat$P_psi_av),
                                  c(rep("C_psi_av",nrow(prot_imm_dat)),rep("P_psi_av",nrow(prot_imm_dat))))
colnames(prot_imm_dat_linear_psi)<- c("Mean_psi","Treatment")

ggplot(prot_imm_dat_linear_psi,aes(y=Mean_psi,x=seq(nrow(prot_imm_dat_linear_psi))))+geom_point(aes(color=Treatment))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

my_comparisons <- list( c("C_psi_av", "P_psi_av"))
ggplot(prot_imm_dat_linear_psi,aes(y=Mean_psi,x=Treatment))+geom_violin(aes(fill=Treatment))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  stat_compare_means(comparisons = my_comparisons)

# ggplot(prot_imm_dat_linear_psi,aes(y=Mean_psi,x=Treatment,group=protein,color=protein))+
#   geom_point()+geom_line()+theme(legend.position = "none")
# 
# ggplot(prot_imm_dat_linear_psi,aes(y=Mean_psi,x=log2(Imm_count+1)))+geom_point(aes(color=Treatment))+
#   geom_smooth(method = "lm")+
#   stat_cor(method = "spearman")

prot_imm_dat_linear_counts <- data.frame(
                                  c(prot_imm_dat$C_norm_counts,prot_imm_dat$P_norm_counts,prot_imm_dat$U_norm_counts),
                                  c(prot_imm_dat$C_norm_counts_med,prot_imm_dat$P_norm_counts_med,prot_imm_dat$U_norm_counts_med),
                                  c(rep("C_norm_counts",nrow(prot_imm_dat)),
                                    rep("P_norm_counts",nrow(prot_imm_dat)),
                                    rep("U_norm_counts",nrow(prot_imm_dat))))
colnames(prot_imm_dat_linear_counts)<- c("Mean_counts","Median_counts","Treatment")

# ggplot(prot_imm_dat_linear_counts,aes(y=Mean_counts,x=protein))+geom_point(aes(color=Treatment))+
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

my_comparisons <- list( c("C_norm_counts", "P_norm_counts"),c("P_norm_counts", "U_norm_counts"),c("C_norm_counts", "U_norm_counts"))
ggplot(prot_imm_dat_linear_counts,aes(y=Mean_counts,x=Treatment))+geom_violin(aes(fill=Treatment))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  stat_compare_means(comparisons = my_comparisons)

# ggplot(prot_imm_dat_linear_counts,aes(y=Mean_counts,x=Treatment,group=protein,color=protein))+
#   geom_point()+geom_line()+theme(legend.position = "none")

# ggplot(prot_imm_dat_linear_counts,aes(y=Mean_counts,x=log2(Imm_count+1)))+geom_point(aes(color=Treatment))+
#   geom_smooth(method = "lm")+
#   stat_cor(method = "spearman")

ggplot(prot_imm_dat,aes(x=counts_order,fill=counts_order))+
  geom_bar(aes(y=(..count..)/sum(..count..)))+
  theme(axis.text.x=element_blank())

ggplot(prot_imm_dat,aes(x=counts_order,fill=counts_order))+
  geom_bar()+
  theme(axis.text.x=element_blank())


# ggplot(prot_imm_dat_linear_counts,aes(y=Median_counts,x=protein))+geom_point(aes(color=Treatment))+
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

my_comparisons <- list( c("C_norm_counts", "P_norm_counts"),c("P_norm_counts", "U_norm_counts"),c("C_norm_counts", "U_norm_counts"))
ggplot(prot_imm_dat_linear_counts,aes(y=Median_counts,x=Treatment))+geom_violin(aes(fill=Treatment))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  stat_compare_means(comparisons = my_comparisons)

# ggplot(prot_imm_dat_linear_counts,aes(y=Median_counts,x=Treatment,group=protein,color=protein))+
#   geom_point()+geom_line()+theme(legend.position = "none")

# ggplot(prot_imm_dat_linear_counts,aes(y=Median_counts,x=log2(Imm_count+1)))+geom_point(aes(color=Treatment))+
#   geom_smooth(method = "lm")+
#   stat_cor(method = "spearman")

ggplot(prot_imm_dat,aes(x=counts_order_med,fill=counts_order_med))+
  geom_bar(aes(y=(..count..)/sum(..count..)))+
  theme(axis.text.x=element_blank())

ggplot(prot_imm_dat,aes(x=counts_order_med,fill=counts_order_med))+
  geom_bar()+
  theme(axis.text.x=element_blank())

```






